---
title: "Voter Registration Analyses Primary DVs"
author: "Katherine Mason"
format: html
editor: source
---

############################################### Prepare Data ############################################### 

```{r, Load Packages}

library(tidyverse)
library(readxl)
library(writexl)
library(openxlsx)
library(psych)
library(ltm)
library(Hmisc)
library(reticulate)
library(nlme)
library(ordinal)
library(carData)
library(car)
library(lme4)
library(lmerTest)
library(lmtest)
library(clubSandwich)
library(sandwich)
library(CR2)
library(lsmeans)
library(stats)
library(sjPlot)
library(sjmisc)
library(ggplot2)
library(glmmTMB) 
library(MASS)
library(broom) 
library(knitr)
library(tools)
library(sjstats)
library(effectsize)
library(pscl)
library(logistf)
library(lavaan)
library(kableExtra)
library(boot)
library(margins)
library(purrr)
library(xtable)
library(gt) 
library(weights)
library(mediation)
library(QuantPsyc)
library(lm.beta)
library(parameters)
library(esc)
library(corrplot)
library(ivreg)
library(BayesFactor)

```

```{r, Load and Prepare Data}

df <- read.csv("Voter_Reg_STRICT.csv")
head(df)

nrow(df) # 12896

zdf <- read.csv("Voter_Reg_STRICT_STANDARDIZED.csv")
head(zdf)

nrow(zdf)

## Prepare variables ##

# Set reference level as the control conditon
df$condition <- relevel(as.factor(df$condition), ref = "ControlCondition")

zdf$condition <- relevel(as.factor(zdf$condition), ref = "ControlCondition")

# Make sure link click, register, and vote variables are factors for binary logistic regressions
df$linkClicked <- as.factor(df$linkClicked)
df$register <- as.factor(df$register)
df$vote <- as.factor(df$vote)

# Region
df$region <- relevel(as.factor(df$region), ref = "Northeast") 

```

################################################################################################################
############################################### Voting Intentions ##############################################
################################################################################################################

# OLS

```{r, Voting Intentions One-Tailed}

# Fit the model 
Intentions_Model_1 <- lm(voteInt ~ condition, data = df)
summary(Intentions_Model_1)

Intentions_Model_1_robust <- coeftest(Intentions_Model_1, vcov = vcovHC(Intentions_Model_1, type = "HC3"))
Intentions_Model_1_robust

Intentions_Model_1_Stand <- lm(voteInt ~ condition, data = zdf)
summary(Intentions_Model_1_Stand)

# Use one tailed lm function to format
Intentions_Model_1_Results <- format_lm_output_onetailed(Intentions_Model_1_robust, Intentions_Model_1_Stand)

# Outputs:
Intentions_Model_1_Results$appendix   # Cleaned and formatted for LaTeX

# Go to BH section for full Latex output 

# Plot percentages within each condition (do not use bs from function here)
Intentions_Model_1_Results_plot <- as.data.frame(emmeans(Intentions_Model_1, ~ condition, level = 0.90)) %>%
  rename(Condition = condition) %>%
    mutate(
    Mean = emmean,
    Lower_ci = lower.CL,
    Upper_ci = upper.CL
  ) %>%
dplyr::select(Condition, Mean, Lower_ci, Upper_ci) 

rownames(Intentions_Model_1_Results_plot) <- NULL

Intentions_Model_1_Results_plot

# write.csv(Intentions_Model_1_Results_plot, file = "Intentions_Percent.csv")

```

# Tukey

```{r, Voting Intentions Tukey Adjustment}

##### Adjust p ####

# Escalating Commitment as the reference condition

df$condition_ec <- factor(df$condition,
  levels = c("EscalatingCommitment", "ControlCondition", "AntiGovernment", "SystemJustification",
             "PersonalImportance", "CorrectingMisperceptions", "DynamicNorms", "ImplementationIntentions",
             "InterdependentConstrual", "MoralReasons", "SelfGeneratedNorms")
)

Intentions_Model_1_EC <- lm(voteInt ~ condition_ec, data = df)
summary(Intentions_Model_1_EC)

# Marginal means
emm_int <- emmeans(Intentions_Model_1_EC, ~ condition_ec)

# Tukey-adjusted pairwise comparisons
tukey_int <- as.data.frame(summary(pairs(emm_int, adjust = "Tukey")))

# One-tailed p

tukey_int$p <- ifelse(
  tukey_int$estimate > 0,  
  tukey_int$p.value / 2,
  1 - tukey_int$p.value / 2
)

tukey_int

# Keep relevant comparisons 
ec_int <- tukey_int %>%
  filter(grepl("EscalatingCommitment", contrast))

# Apply formatting and sorting
ec_int_clean <- ec_int %>%
  mutate(
    Contrast = contrast,
    Estimate = sprintf("%.2f", estimate),
    SE = sprintf("%.2f", SE),
    t = sprintf("%.2f", t.ratio),
    p = ifelse(p < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p))),
    p.value_two = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value)))) %>%
    dplyr::select(Contrast, Estimate, SE, t, p) %>%
    filter(!Contrast == 'EscalatingCommitment - ControlCondition') # Control condition not needed

ec_int_clean

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r")

ec_int_clean_appendix_xtable <- xtable(ec_int_clean, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(ec_int_clean_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Mixed Model Accounting for Within-state Non-independence

```{r, Voting Intentions MLM Robustness Check One-Tailed}

# Fit the model
Intentions_Model_2 <- lmer(voteInt ~ condition + (1 | state), data = df)
summary(Intentions_Model_2)

Intentions_Model_2_Stand <- lmer(voteInt ~ condition + (1 | state), data = zdf)
summary(Intentions_Model_2_Stand)

# Use one tailed linear MLM function to format
Intentions_Model_2_Results <- format_linear_mixed_output_onetailed(Intentions_Model_2, Intentions_Model_2_Stand)

# Outputs:
Intentions_Model_2_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_2_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# With Covariates

```{r, Voting Intentions with Covariates One-Tailed (Pre-registered)}

# Fit the model 
Intentions_Model_3 <- lm(voteInt ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = df)
summary(Intentions_Model_3)

Intentions_Model_3_robust <- coeftest(Intentions_Model_3, vcov = vcovHC(Intentions_Model_3, type = "HC3"))
Intentions_Model_3_robust 

Intentions_Model_3_Stand <- lm(voteInt ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = zdf)
summary(Intentions_Model_3_Stand)

# Use one tailed lm function to format
Intentions_Model_3_Results <- format_lm_output_onetailed(Intentions_Model_3_robust, Intentions_Model_3_Stand)

# Outputs:
Intentions_Model_3_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_3_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# OLS - All Legs

```{r, Intentions All Legs One-Tailed}

# Fit the model (use OLS)
Intentions_Model_4 <- lm(voteInt ~ condition_binary, data = df) 
summary(Intentions_Model_4)

Intentions_Model_4_robust <- coeftest(Intentions_Model_4, vcov = vcovHC(Intentions_Model_4, type = "HC3"))

Intentions_Model_4_Stand <- lm(voteInt ~ condition_binary, data = zdf) 
summary(Intentions_Model_4_Stand)

# Use one tailed lm function to format
Intentions_Model_4_Results <- format_lm_output_onetailed(Intentions_Model_4_robust, Intentions_Model_4_Stand)

# Outputs:
Intentions_Model_4_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_4_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

############# Voting Intentions Moderations (two-tailed)

# Demographics

```{r, Voting Intentions Interaction with Ideology Two-Tailed}

# Test the interaction with ideology
Intentions_Model_4 <- lm(voteInt ~ condition*ide_c, data = df)
summary(Intentions_Model_4)

Intentions_Model_4_robust <- coeftest(Intentions_Model_4, vcov = vcovHC(Intentions_Model_4, type = "HC3"))
Intentions_Model_4_robust

Intentions_Model_4_Stand <- lm(voteInt ~ condition*ide_c, data = zdf)
summary(Intentions_Model_4_Stand)

# Use two tailed lm function to format
Intentions_Model_4_Results <- format_lm_output_twotailed(Intentions_Model_4_robust, Intentions_Model_4_Stand)

# Outputs:
Intentions_Model_4_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_4_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Voting Intentions Interaction with Gender Two-Tailed}

# Condition*gender
Intentions_Model_5 <- lm(voteInt ~ condition*gend_e, data = df)
summary(Intentions_Model_5) 

Intentions_Model_5_robust <- coeftest(Intentions_Model_5, vcov = vcovHC(Intentions_Model_5, type = "HC3"))
Intentions_Model_5_robust

Intentions_Model_5_Stand <- lm(voteInt ~ condition*gend_e, data = zdf)
summary(Intentions_Model_5_Stand) 

# Use two tailed lm function to format
Intentions_Model_5_Results <- format_lm_output_twotailed(Intentions_Model_5_robust, Intentions_Model_5_Stand)

# Outputs:
Intentions_Model_5_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_5_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Voting Intentions Interaction with Race Two-Tailed}

# Condition*race 
Intentions_Model_6 <- lm(voteInt ~ condition*race_bin_e, data = df)
summary(Intentions_Model_6)

Intentions_Model_6_robust <- coeftest(Intentions_Model_6, vcov = vcovHC(Intentions_Model_6, type = "HC3"))
Intentions_Model_6_robust

Intentions_Model_6_Stand <- lm(voteInt ~ condition*race_bin_e, data = zdf)
summary(Intentions_Model_6_Stand)

# Use two tailed lm function to format
Intentions_Model_6_Results <- format_lm_output_twotailed(Intentions_Model_6_robust, Intentions_Model_6_Stand)

# Outputs:
Intentions_Model_6_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_6_Results$appendix_xtable, include.rownames = FALSE, longtable = TRUE) # Syntax for latex editor

##

# White participants

Intentions_Model_7 <- lm(voteInt ~ condition*race_bin, data = df)
summary(Intentions_Model_7)

Intentions_Model_7_robust <- coeftest(Intentions_Model_7, vcov = vcovHC(Intentions_Model_7, type = "HC3"))
Intentions_Model_7_robust

Intentions_Model_7_Stand <- lm(voteInt ~ condition*race_bin, data = zdf)
summary(Intentions_Model_7_Stand)

# Use two tailed lm function to format
Intentions_Model_7_Results <- format_lm_output_twotailed(Intentions_Model_7_robust, Intentions_Model_7_Stand)

Intentions_Model_7_Results$appendix 

##

# Non-White participants

Intentions_Model_8 <- lm(voteInt ~ condition*race_bin_r, data = df)
summary(Intentions_Model_8)

Intentions_Model_8_robust <- coeftest(Intentions_Model_8, vcov = vcovHC(Intentions_Model_8, type = "HC3"))
Intentions_Model_8_robust

Intentions_Model_8_Stand <- lm(voteInt ~ condition*race_bin_r, data = zdf)
summary(Intentions_Model_8_Stand)

# Use two tailed lm function to format
Intentions_Model_8_Results <- format_lm_output_twotailed(Intentions_Model_8_robust, Intentions_Model_8_Stand)

Intentions_Model_8_Results$appendix 

```

```{r, Voting Intentions Interaction with Age Two-Tailed}

# Condition*age
Intentions_Model_9 <- lm(voteInt ~ condition*age_c, data = df)
summary(Intentions_Model_9) 

Intentions_Model_9_robust <- coeftest(Intentions_Model_9, vcov = vcovHC(Intentions_Model_9, type = "HC3"))
Intentions_Model_9_robust

Intentions_Model_9_Stand <- lm(voteInt ~ condition*age_c, data = zdf)
summary(Intentions_Model_9_Stand) 

# Use two tailed lm function to format
Intentions_Model_9_Results <- format_lm_output_twotailed(Intentions_Model_9_robust, Intentions_Model_9_Stand)

# Outputs:
Intentions_Model_9_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_9_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Voting Intentions Interaction with Income Two-Tailed}

# Condition*income
Intentions_Model_10 <- lm(voteInt ~ condition*income_c, data = df)
summary(Intentions_Model_10) 

Intentions_Model_10_robust <- coeftest(Intentions_Model_10, vcov = vcovHC(Intentions_Model_10, type = "HC3"))
Intentions_Model_10_robust

Intentions_Model_10_Stand <- lm(voteInt ~ condition*income_c, data = zdf)
summary(Intentions_Model_10_Stand) 

# Use two tailed lm function to format
Intentions_Model_10_Results <- format_lm_output_twotailed(Intentions_Model_10_robust, Intentions_Model_10_Stand)

# Outputs:
Intentions_Model_10_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_10_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Voting Intentions Interaction with Education Two-Tailed}

# Condition*education
Intentions_Model_11 <- lm(voteInt ~ condition*edu_c, data = df)
summary(Intentions_Model_11) 

Intentions_Model_11_robust <- coeftest(Intentions_Model_11, vcov = vcovHC(Intentions_Model_11, type = "HC3"))
Intentions_Model_11_robust

Intentions_Model_11_Stand <- lm(voteInt ~ condition*edu_c, data = zdf)
summary(Intentions_Model_11_Stand) 

# Use two tailed lm function to format
Intentions_Model_11_Results <- format_lm_output_twotailed(Intentions_Model_11_robust, Intentions_Model_11_Stand)

# Outputs:
Intentions_Model_11_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_11_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

##

# Low education

Intentions_Model_12 <- lm(voteInt ~ condition*edu_low, data = df)
summary(Intentions_Model_12) 

Intentions_Model_12_robust <- coeftest(Intentions_Model_12, vcov = vcovHC(Intentions_Model_12, type = "HC3"))
Intentions_Model_12_robust

Intentions_Model_12_Stand <- lm(voteInt ~ condition*edu_low, data = zdf)
summary(Intentions_Model_12_Stand) 

# Use two tailed lm function to format
Intentions_Model_12_Results <- format_lm_output_twotailed(Intentions_Model_12_robust, Intentions_Model_12_Stand)

# Outputs:
Intentions_Model_12_Results$appendix 

##

# High education

Intentions_Model_13 <- lm(voteInt ~ condition*edu_high, data = df)
summary(Intentions_Model_13) 

Intentions_Model_13_robust <- coeftest(Intentions_Model_13, vcov = vcovHC(Intentions_Model_13, type = "HC3"))
Intentions_Model_13_robust

Intentions_Model_13_Stand <- lm(voteInt ~ condition*edu_high, data = zdf)
summary(Intentions_Model_13_Stand) 

# Use two tailed lm function to format
Intentions_Model_13_Results <- format_lm_output_twotailed(Intentions_Model_13_robust, Intentions_Model_13_Stand)

# Outputs:
Intentions_Model_13_Results$appendix 

```

# Pre-Intention to Register

```{r, Intentions to Vote Interaction with Pre-Intention to Register Two-Tailed}

# Test the interaction with pre-intention to register
Intentions_Model_14 <- lm(voteInt ~ condition*pre_intention_c, data = df)
summary(Intentions_Model_14)

Intentions_Model_14_robust <- coeftest(Intentions_Model_14, vcov = vcovHC(Intentions_Model_14, type = "HC3"))
Intentions_Model_14_robust

Intentions_Model_14_Stand <- lm(voteInt ~ condition*pre_intention_c, data = zdf)
summary(Intentions_Model_14_Stand)

# Use two tailed lm function to format
Intentions_Model_14_Results <- format_lm_output_twotailed(Intentions_Model_14_robust, Intentions_Model_14_Stand)

# Outputs:
Intentions_Model_14_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_14_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Interest

```{r, Voting Intentions Interaction with Interest Two-Tailed}

# Test the interaction with interest
Intentions_Model_15 <- lm(voteInt ~ condition*interest_c, data = df)
summary(Intentions_Model_15) 

Intentions_Model_15_robust <- coeftest(Intentions_Model_15, vcov = vcovHC(Intentions_Model_15, type = "HC3"))
Intentions_Model_15_robust 

Intentions_Model_15_Stand <- lm(voteInt ~ condition*interest_c, data = zdf)
summary(Intentions_Model_15_Stand) 

# Use two tailed lm function to format
Intentions_Model_15_Results <- format_lm_output_twotailed(Intentions_Model_15_robust, Intentions_Model_15_Stand)

# Outputs:
Intentions_Model_15_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_15_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Knowledge

```{r, Voting Intentions Interaction with Knowledge Two-Tailed}

# Test the interaction with knowledge 
Intentions_Model_16 <- lm(voteInt ~ condition*knowledge_c, data = df)
summary(Intentions_Model_16) 

Intentions_Model_16_robust <- coeftest(Intentions_Model_16, vcov = vcovHC(Intentions_Model_16, type = "HC3"))
Intentions_Model_16_robust 

Intentions_Model_16_Stand <- lm(voteInt ~ condition*knowledge_c, data = zdf)
summary(Intentions_Model_16_Stand) 

# Use two tailed lm function to format
Intentions_Model_16_Results <- format_lm_output_twotailed(Intentions_Model_16_robust, Intentions_Model_16_Stand)

# Outputs:
Intentions_Model_16_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_16_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# By Region

```{r, Voting Intentions Interaction with Region Two-Tailed}

# Interaction with region
Intentions_Model_17 <- lm(voteInt~ condition*region, data = df)
summary(Intentions_Model_17) 

# Means within each region
intmeansregion <- emmeans(Intentions_Model_17, ~ condition | region, level = 0.95)

# Condition differences by region
intcomparecond <- as.data.frame(pairs(intmeansregion, adjust = "None", by = "region")) %>%
  filter(grepl("ControlCondition", contrast)) # Only keep comparisons with the control condition

intcomparecond

# Apply formatting and sorting
intcomparecond_clean <- intcomparecond %>%
  mutate(
    Contrast = contrast,
    b = sprintf("%.2f", -1*estimate),
    SE = sprintf("%.2f", SE),
    t = sprintf("%.2f", -1*t.ratio),
    p = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value))),
    p.value_two = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value)))) %>%
    dplyr::select(Contrast, b, SE, t, p)

intcomparecond_clean

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r")

intcomparecond_clean_clean_appendix_xtable <- xtable(intcomparecond_clean, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(intcomparecond_clean_clean_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# By Swing State

```{r, Voting Intentions Interaction with Swing State}

# Test the interaction with COVI score
Intentions_Model_18 <- lm(voteInt ~ condition*swing_E, data = df)
summary(Intentions_Model_18) 

Intentions_Model_18_robust <- coeftest(Intentions_Model_18, vcov = vcovHC(Intentions_Model_18, type = "HC3"))
Intentions_Model_18_robust 

Intentions_Model_18_Stand <- lm(voteInt ~ condition*swing_E, data = zdf)
summary(Intentions_Model_18_Stand) 

# Use two tailed glm function to format
Intentions_Model_18_Results <- format_lm_output_twotailed(Intentions_Model_18_robust, Intentions_Model_18_Stand)

# Outputs:
Intentions_Model_18_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_18_Results$appendix_xtable, include.rownames = FALSE)

##

# Non-swing state

Intentions_Model_19 <- lm(voteInt ~ condition*swing, data = df)
summary(Intentions_Model_19) 

Intentions_Model_19_robust <- coeftest(Intentions_Model_19, vcov = vcovHC(Intentions_Model_19, type = "HC3"))
Intentions_Model_19_robust 

Intentions_Model_19_Stand <- lm(voteInt ~ condition*swing, data = zdf)
summary(Intentions_Model_19_Stand) 

# Use two tailed glm function to format
Intentions_Model_19_Results <- format_lm_output_twotailed(Intentions_Model_19_robust, Intentions_Model_19_Stand)

# Outputs:
Intentions_Model_19_Results$appendix   # Cleaned and formatted for LaTeX


##

# Swing state
Intentions_Model_20 <- lm(voteInt ~ condition*swing_r, data = df)
summary(Intentions_Model_20) 

Intentions_Model_20_robust <- coeftest(Intentions_Model_20, vcov = vcovHC(Intentions_Model_20, type = "HC3"))
Intentions_Model_20_robust 

Intentions_Model_20_Stand <- lm(voteInt ~ condition*swing_r, data = zdf)
summary(Intentions_Model_20_Stand) 

# Use two tailed glm function to format
Intentions_Model_20_Results <- format_lm_output_twotailed(Intentions_Model_20_robust, Intentions_Model_20_Stand)

# Outputs:
Intentions_Model_20_Results$appendix   # Cleaned and formatted for LaTeX

```

# Cost of Voting Index (COVI)

```{r, Voting Intentions Interaction with COVI Two-Tailed}

# Test the interaction with COVI score
Intentions_Model_21 <- lm(voteInt ~ condition*COVI_c, data = df)
summary(Intentions_Model_21) 

Intentions_Model_21_robust <- coeftest(Intentions_Model_21, vcov = vcovHC(Intentions_Model_21, type = "HC3"))
Intentions_Model_21_robust 

Intentions_Model_21_Stand <- lm(voteInt ~ condition*COVI_c, data = zdf)
summary(Intentions_Model_21_Stand) 

# Use two tailed glm function to format
Intentions_Model_21_Results <- format_lm_output_twotailed(Intentions_Model_21_robust, Intentions_Model_21_Stand)

# Outputs:
Intentions_Model_21_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Intentions_Model_21_Results$appendix_xtable, include.rownames = FALSE)

```

################################################################################################################
################################################## Link Clicks #################################################
################################################################################################################

# OLS

```{r, Link Click One-Tailed}

# Fit the model (use OLS)
Link_Model_1 <- lm(linkClicked_n ~ condition, data = df) 
summary(Link_Model_1)

Link_Model_1_robust <- coeftest(Link_Model_1, vcov = vcovHC(Link_Model_1, type = "HC3"))
Link_Model_1_robust

Link_Model_1_Stand <- lm(linkClicked_n ~ condition, data = zdf) 
summary(Link_Model_1_Stand)

# Use one tailed lm function to format
Link_Model_1_Results <- format_lm_bin_output_onetailed(Link_Model_1_robust, Link_Model_1_Stand)

# Outputs:
Link_Model_1_Results$appendix   # Cleaned and formatted for LaTeX

# Go to BH section for full Latex output 

# Plot percentages within each condition
Link_Model_1_Results_plot <- as.data.frame(emmeans(Link_Model_1, ~ condition, level = 0.90)) %>%
  rename(Condition = condition) %>%
    mutate(
    Mean = emmean*100,
    Lower_ci = lower.CL*100,
    Upper_ci = upper.CL*100
  ) %>%
dplyr::select(Condition, Mean, Lower_ci, Upper_ci) 

rownames(Link_Model_1_Results_plot) <- NULL

Link_Model_1_Results_plot

# write.csv(Link_Model_1_Results_plot, file = "Link_Percent.csv")

```

# Tukey

```{r, Link Click Tukey Adjustment}

##### Adjust p ####

# Escalating Commitment as the reference condition

df$condition_ec <- factor(df$condition,
  levels = c("EscalatingCommitment", "ControlCondition", "AntiGovernment", "SystemJustification",
             "PersonalImportance", "CorrectingMisperceptions", "DynamicNorms", "ImplementationIntentions",
             "InterdependentConstrual", "MoralReasons", "SelfGeneratedNorms")
)

# Fit the model (use OLS)
Link_Model_1_EC <- lm(linkClicked_n ~ condition_ec, data = df) 
summary(Link_Model_1_EC)

# Marginal means
emm_link <- emmeans(Link_Model_1_EC, ~ condition_ec)

# Tukey-adjusted pairwise comparisons
tukey_link <- as.data.frame(summary(pairs(emm_link, adjust = "Tukey")))

# One-tailed p
tukey_link$p <- ifelse(
  tukey_link$estimate > 0,  
  tukey_link$p.value / 2,
  1 - tukey_link$p.value / 2
)

tukey_link

# Keep relevant comparisons
ec_link <- tukey_link %>%
  filter(grepl("EscalatingCommitment", contrast))

ec_link_clean <- ec_link %>% 
  mutate(
    Contrast = contrast,
    'PP Inc.' = sprintf("%.2f", 100*estimate),
    b = sprintf("%.2f", estimate),
    SE = sprintf("%.2f", SE),
    t = sprintf("%.2f", t.ratio),
    p = ifelse(p < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p))), # one tailed
    p.value_two = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value)))) %>%
  dplyr::select(Contrast, 'PP Inc.', b, SE, t, p) %>%
  filter(!Contrast == 'EscalatingCommitment - ControlCondition') # Control condition not needed

ec_link_clean

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r", "r")

ec_link_clean_xtable <- xtable(ec_link_clean, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(ec_link_clean_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Logit

```{r, Link Click One-Tailed (Logit)}

# Fit the model (use logit)
Link_Model_2 <- glm(linkClicked ~ condition, data = df, family = binomial(link = "logit"))
summary(Link_Model_2)
  
Link_Model_2_robust <- coeftest(Link_Model_2, vcov = vcovHC(Link_Model_2, type = "HC3"))

# saveRDS(Link_Model_2_robust, "Link_Model_LOGIT.rds")

# Use one tailed glm function to format
Link_Model_2_Results <- format_logit_output_onetailed(Link_Model_2_robust)

# Outputs:
Link_Model_2_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_2_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Firth's Penalized Regression

```{r, Link Click Firth's Robustness Check One-Tailed}

# Firth’s penalized logistic regression reduces bias in logistic regression with imbalanced data (i.e., more 0s than 1s)

Link_Model_3 <- logistf(data=df, linkClicked~condition)
summary(Link_Model_3)

# Extract coefficients, standard errors, p-values, and confidence intervals
coefs <- coef(Link_Model_3)
se <- sqrt(diag(Link_Model_3$var))
p_values <- (Link_Model_3$prob)/2
conf_int <- confint(Link_Model_3, level = .90)

# Create a data frame 
Link_Model_3_Results <- data.frame(
  Variable = gsub("condition", "", names(coefs)),
  Log_Odds = coefs,
  OR = exp(coefs),
  SE_LO = se,
  SE = exp(se),
  p = p_values,
  Lower_ci_LO = conf_int[, 1],
  Upper_ci_LO = conf_int[, 2],
  Lower_ci = exp(conf_int[, 1]),
  Upper_ci = exp(conf_int[, 2])
)

rownames(Link_Model_3_Results) <- NULL

# Clean up
Link_Model_3_Results <- Link_Model_3_Results %>%
  mutate(
    Variable = dplyr::recode(Variable, !!!variable_labels), # Edit variable names
    Log_Odds = sprintf("%.2f", Log_Odds), # Round 
    OR = sprintf("%.2f", OR), 
    SE_LO = sprintf("%.2f", SE_LO),
    SE = sprintf("%.2f", SE),
    p = ifelse(p < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p))), 
    Lower_ci_LO = sprintf("%.2f", Lower_ci_LO), # CI in brackets
    Upper_ci_LO = sprintf("%.2f", Upper_ci_LO),
    `90% CI` = paste0("[", Lower_ci_LO, ", ", Upper_ci_LO, "]"),
    Lower_ci = sprintf("%.2f", Lower_ci), 
    Upper_ci = sprintf("%.2f", Upper_ci),
    `90% CI` = paste0("[", Lower_ci, ", ", Upper_ci, "]")
        
) %>%
    dplyr::select(Variable,
         OR, SE, p, `90% CI`)

Link_Model_3_Results

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r")
Link_Model_3_Results_appendix_xtable <- xtable(Link_Model_3_Results, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(Link_Model_3_Results_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Mixed Model Accounting for Within-state Non-independence

```{r, Link Click MLM Robustness Check One-Tailed}

# Fit the model
Link_Model_4 <- lmer(linkClicked_n ~ condition + (1 | state), data = df)
summary(Link_Model_4)

Link_Model_4_Stand <- lmer(linkClicked_n ~ condition + (1 | state), data = zdf)
summary(Link_Model_4_Stand)

# Use one tailed lm MLM function to format 
Link_Model_4_Results <- format_linear_mixed_bin_output_onetailed(Link_Model_4, Link_Model_4_Stand)

# Outputs:
Link_Model_4_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_4_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# OLS with Covariates

```{r, Link Click One-Tailed with Covariates}

# Fit the model (use OLS)
Link_Model_5 <- lm(linkClicked_n ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = df) 
summary(Link_Model_5)

Link_Model_5_robust <- coeftest(Link_Model_5, vcov = vcovHC(Link_Model_5, type = "HC3"))

Link_Model_5_Stand <- lm(linkClicked_n ~ condition + + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = zdf) 
summary(Link_Model_5_Stand)

# Use one tailed glm function to format
Link_Model_5_Results <- format_lm_bin_output_onetailed(Link_Model_5_robust, Link_Model_5_Stand)

# Outputs:
Link_Model_5_Results$appendix   

# Go to BH section for full Latex output

# Plot percentages within each condition
Link_Model_5_Results_plot <- as.data.frame(emmeans(Link_Model_5, ~ condition, level = 0.90)) %>%
  rename(Condition = condition) %>%
    mutate(
    Mean = emmean*100,
    Lower_ci = lower.CL*100,
    Upper_ci = upper.CL*100
  ) %>%
dplyr::select(Condition, Mean, Lower_ci, Upper_ci) 

rownames(Link_Model_5_Results_plot) <- NULL

Link_Model_5_Results_plot

# write.csv(Link_Model_5_Results_plot, file = "Link_Percent_Covs.csv")

```

# Logit with Covariates (Pre-registered)

```{r, Link Click One-Tailed with Covariates}

# Fit the model (use logit)
Link_Model_5 <- glm(linkClicked ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = df, family = binomial(link = "logit")) 
summary(Link_Model_5)

Link_Model_5_robust <- coeftest(Link_Model_5, vcov = vcovHC(Link_Model_5, type = "HC3"))

# Use one tailed glm function to format
Link_Model_5_Results <- format_logit_output_onetailed(Link_Model_5_robust)

# Outputs:
Link_Model_5_Results$appendix   

print.xtable(Link_Model_5_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# OLS - All Legs

```{r, Link Click All Legs One-Tailed}

# Fit the model (use OLS)
Link_Model_6 <- lm(linkClicked_n ~ condition_binary, data = df) 
summary(Link_Model_6)

Link_Model_6_robust <- coeftest(Link_Model_6, vcov = vcovHC(Link_Model_6, type = "HC3"))

Link_Model_6_Stand <- lm(linkClicked_n ~ condition_binary, data = zdf) 
summary(Link_Model_6_Stand)

# Use one tailed lm function to format
Link_Model_6_Results <- format_lm_bin_output_onetailed(Link_Model_6_robust, Link_Model_6_Stand)

# Outputs:
Link_Model_6_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_6_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

############# Link Clicks Moderations (two-tailed)

# Demographics

```{r, Link Clicks Interaction with Ideology Two-Tailed}

# Test the interaction with ideology
Link_Model_7 <- lm(linkClicked_n ~ condition*ide_c, data = df)
summary(Link_Model_7) 

Link_Model_7_robust <- coeftest(Link_Model_7, vcov = vcovHC(Link_Model_7, type = "HC3"))
Link_Model_7_robust 

Link_Model_7_Stand <- lm(linkClicked_n ~ condition*ide_c, data = zdf)
summary(Link_Model_7_Stand) 

# Use two tailed lm function to format
Link_Model_7_Results <- format_lm_bin_output_twotailed(Link_Model_7_robust, Link_Model_7_Stand)

# Outputs:
Link_Model_7_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_7_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Link Clicks Interaction with Gender Two-Tailed}

# Condition*gender
Link_Model_8 <- lm(linkClicked_n ~ condition*gend_e, data = df)
summary(Link_Model_8)

Link_Model_8_robust <- coeftest(Link_Model_8, vcov = vcovHC(Link_Model_8, type = "HC3"))
Link_Model_8_robust 

Link_Model_8_Stand <- lm(linkClicked_n ~ condition*gend_e, data = zdf)
summary(Link_Model_8_Stand)

# Use two tailed lm function to format
Link_Model_8_Results <- format_lm_bin_output_twotailed(Link_Model_8_robust, Link_Model_8_Stand)

# Outputs:
Link_Model_8_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_8_Results$appendix_xtable, include.rownames = FALSE)

# Men

# Condition*gender
Link_Model_9 <- lm(linkClicked_n ~ condition*gend_bin, data = df)
summary(Link_Model_9)

Link_Model_9_robust <- coeftest(Link_Model_9, vcov = vcovHC(Link_Model_9, type = "HC3"))
Link_Model_9_robust 

Link_Model_9_Stand <- lm(linkClicked_n ~ condition*gend_bin, data = zdf)
summary(Link_Model_9_Stand)

# Use two tailed lm function to format
Link_Model_9_Results <- format_lm_bin_output_twotailed(Link_Model_9_robust, Link_Model_9_Stand)

# Outputs:
Link_Model_9_Results$appendix   # Cleaned and formatted for LaTeX

# Women

Link_Model_10 <- lm(linkClicked_n ~ condition*gend_bin_r, data = df)
summary(Link_Model_10)

Link_Model_10_robust <- coeftest(Link_Model_10, vcov = vcovHC(Link_Model_10, type = "HC3"))
Link_Model_10_robust 

Link_Model_10_Stand <- lm(linkClicked_n ~ condition*gend_bin_r, data = zdf)
summary(Link_Model_10_Stand)

# Use two tailed lm function to format
Link_Model_10_Results <- format_lm_bin_output_twotailed(Link_Model_10_robust, Link_Model_10_Stand)

# Outputs:
Link_Model_10_Results$appendix   # Cleaned and formatted for LaTeX

```

```{r, Link Clicks Interaction with Race Two-Tailed}

# Condition*race (binary)
Link_Model_11 <- lm(linkClicked_n ~ condition*race_bin_e, data = df)
summary(Link_Model_11) 

Link_Model_11_robust <- coeftest(Link_Model_11, vcov = vcovHC(Link_Model_11, type = "HC3"))
Link_Model_11_robust 

Link_Model_11_Stand <- lm(linkClicked_n ~ condition*race_bin_e, data = zdf)
summary(Link_Model_11_Stand) 

# Use two tailed lm function to format
Link_Model_11_Results <- format_lm_bin_output_twotailed(Link_Model_11_robust, Link_Model_11_Stand)

# Outputs:
Link_Model_11_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_11_Results$appendix_xtable, include.rownames = FALSE, longtable = TRUE) # Syntax for latex editor

```

```{r, Link Clicks Interaction with Age Two-Tailed}

# Condition*age
Link_Model_12 <- lm(linkClicked_n ~ condition*age_c, data = df)
summary(Link_Model_12) 

Link_Model_12_robust <- coeftest(Link_Model_12, vcov = vcovHC(Link_Model_12, type = "HC3"))
Link_Model_12_robust 

Link_Model_12_Stand <- lm(linkClicked_n ~ condition*age_c, data = zdf)
summary(Link_Model_12_Stand) 

# Use two tailed glm function to format
Link_Model_12_Results <- format_lm_bin_output_twotailed(Link_Model_12_robust, Link_Model_12_Stand)

# Outputs:
Link_Model_12_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_12_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Link Clicks Interaction with Income Two-Tailed}

# Condition*income
Link_Model_13 <- lm(linkClicked_n ~ condition*income_c, data = df)
summary(Link_Model_13) 

Link_Model_13_robust <- coeftest(Link_Model_13, vcov = vcovHC(Link_Model_13, type = "HC3"))
Link_Model_13_robust

Link_Model_13_Stand <- lm(linkClicked_n ~ condition*income_c, data = zdf)
summary(Link_Model_13_Stand) 

# Use two tailed lm function to format
Link_Model_13_Results <- format_lm_bin_output_twotailed(Link_Model_13_robust, Link_Model_13_Stand)

# Outputs:
Link_Model_13_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_13_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

##

# Low income

Link_Model_14 <- lm(linkClicked_n ~ condition*income_low, data = df)
summary(Link_Model_14) 

Link_Model_14_robust <- coeftest(Link_Model_14, vcov = vcovHC(Link_Model_14, type = "HC3"))
Link_Model_14_robust 

Link_Model_14_Stand <- lm(linkClicked_n ~ condition*income_low, data = zdf)
summary(Link_Model_14_Stand) 

# Use two tailed lm function to format
Link_Model_14_Results <- format_lm_bin_output_twotailed(Link_Model_14_robust, Link_Model_14_Stand)

# Outputs:
Link_Model_14_Results$appendix 
 
##

# High income

Link_Model_15 <- lm(linkClicked_n ~ condition*income_high, data = df)
summary(Link_Model_15) 

Link_Model_15_robust <- coeftest(Link_Model_15, vcov = vcovHC(Link_Model_15, type = "HC3"))
Link_Model_15_robust 

Link_Model_15_Stand <- lm(linkClicked_n ~ condition*income_high, data = zdf)
summary(Link_Model_15_Stand) 

# Use two tailed lm function to format
Link_Model_15_Results <- format_lm_bin_output_twotailed(Link_Model_15_robust, Link_Model_15_Stand)

# Outputs:
Link_Model_15_Results$appendix   

```

```{r, Link Clicks Interaction with Education Two-Tailed}}

# Condition*education
Link_Model_16 <- lm(linkClicked_n ~ condition*edu_c, data = df)
summary(Link_Model_16) 

Link_Model_16_robust <- coeftest(Link_Model_16, vcov = vcovHC(Link_Model_16, type = "HC3"))
Link_Model_16_robust 

Link_Model_16_Stand <- lm(linkClicked_n ~ condition*edu_c, data = zdf)
summary(Link_Model_16_Stand) 

# Use two tailed lm function to format
Link_Model_16_Results <- format_lm_bin_output_twotailed(Link_Model_16_robust, Link_Model_16_Stand)

# Outputs:
Link_Model_16_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_16_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Pre-Intention to Register

```{r, Link Clicks Interaction with Pre-Intention to Register Two-Tailed}

# Test the interaction with pre-intention to register
Link_Model_17 <- lm(linkClicked_n ~ condition*pre_intention_c, data = df)
summary(Link_Model_17) 

Link_Model_17_robust <- coeftest(Link_Model_17, vcov = vcovHC(Link_Model_17, type = "HC3"))
Link_Model_17_robust 

Link_Model_17_Stand <- lm(linkClicked_n ~ condition*pre_intention_c, data = zdf)
summary(Link_Model_17_Stand) 

# Use two tailed lm function to format
Link_Model_17_Results <- format_lm_bin_output_twotailed(Link_Model_17_robust, Link_Model_17_Stand)

# Outputs:
Link_Model_17_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_17_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

##

# Low intention to register
Link_Model_18 <- lm(linkClicked_n ~ condition*pre_intention_low, data = df)
summary(Link_Model_18) 

Link_Model_18_robust <- coeftest(Link_Model_18, vcov = vcovHC(Link_Model_18, type = "HC3"))
Link_Model_18_robust 

Link_Model_18_Stand <- lm(linkClicked_n ~ condition*pre_intention_low, data = zdf)
summary(Link_Model_18_Stand) 

# Use two tailed lm function to format
Link_Model_18_Results <- format_lm_bin_output_twotailed(Link_Model_18_robust, Link_Model_18_Stand)

# Outputs:
Link_Model_18_Results$appendix   # Cleaned and formatted for LaTeX

##

# High intention to register
Link_Model_19 <- lm(linkClicked_n ~ condition*pre_intention_high, data = df)
summary(Link_Model_19) 

Link_Model_19_robust <- coeftest(Link_Model_19, vcov = vcovHC(Link_Model_19, type = "HC3"))
Link_Model_19_robust 

Link_Model_19_Stand <- lm(linkClicked_n ~ condition*pre_intention_high, data = zdf)
summary(Link_Model_19_Stand) 

# Use two tailed lm function to format
Link_Model_19_Results <- format_lm_bin_output_twotailed(Link_Model_19_robust, Link_Model_19_Stand)

# Outputs:
Link_Model_19_Results$appendix  # Cleaned and formatted for LaTeX

```

# Interest

```{r, Link Clicks Interaction with Interest Two-Tailed}

# Test the interaction with interest
Link_Model_20 <- lm(linkClicked_n ~ condition*interest_c, data = df)
summary(Link_Model_20) 

Link_Model_20_robust <- coeftest(Link_Model_20, vcov = vcovHC(Link_Model_20, type = "HC3"))
Link_Model_20_robust

Link_Model_20_Stand <- lm(linkClicked_n ~ condition*interest_c, data = zdf)
summary(Link_Model_20_Stand) 

# Use two tailed lm function to format
Link_Model_20_Results <- format_lm_bin_output_twotailed(Link_Model_20_robust, Link_Model_20_Stand)

# Outputs:
Link_Model_20_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_20_Results$appendix_xtable, include.rownames = FALSE)

## 

# Low interest
Link_Model_21 <- lm(linkClicked_n ~ condition*interest_low, data = df)
summary(Link_Model_21) 

Link_Model_21_robust <- coeftest(Link_Model_21, vcov = vcovHC(Link_Model_21, type = "HC3"))
Link_Model_21_robust 

Link_Model_21_Stand <- lm(linkClicked_n ~ condition*interest_low, data = zdf)
summary(Link_Model_21_Stand) 

# Use two tailed lm function to format
Link_Model_21_Results <- format_lm_bin_output_twotailed(Link_Model_21_robust, Link_Model_21_Stand)

# Outputs:
Link_Model_21_Results$appendix    

##

# High interest
Link_Model_22 <- lm(linkClicked_n ~ condition*interest_high, data = df)
summary(Link_Model_22) 

Link_Model_22_robust <- coeftest(Link_Model_22, vcov = vcovHC(Link_Model_22, type = "HC3"))
Link_Model_22_robust 

Link_Model_22_Stand <- lm(linkClicked_n ~ condition*interest_high, data = zdf)
summary(Link_Model_22_Stand) 

# Use two tailed lm function to format
Link_Model_22_Results <- format_lm_bin_output_twotailed(Link_Model_22_robust, Link_Model_22_Stand)

# Outputs:
Link_Model_22_Results$appendix   

```

# Knowledge

```{r, Link Clicks Interaction with Knowledge Two-Tailed}

# Test the interaction with knowledge
Link_Model_23 <- lm(linkClicked_n ~ condition*knowledge_c, data = df)
summary(Link_Model_23) 

Link_Model_23_robust <- coeftest(Link_Model_23, vcov = vcovHC(Link_Model_23, type = "HC3"))
Link_Model_23_robust 

Link_Model_23_Stand <- lm(linkClicked_n ~ condition*knowledge_c, data = zdf)
summary(Link_Model_23_Stand)

# Use two tailed lm function to format
Link_Model_23_Results <- format_lm_bin_output_twotailed(Link_Model_23_robust, Link_Model_23_Stand)

# Outputs:
Link_Model_23_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_23_Results$appendix_xtable, include.rownames = FALSE)

## 

# Low knowledge
Link_Model_24 <- lm(linkClicked_n ~ condition*knowledge_low, data = df)
summary(Link_Model_24) 

Link_Model_24_robust <- coeftest(Link_Model_24, vcov = vcovHC(Link_Model_24, type = "HC3"))
Link_Model_24_robust 

Link_Model_24_Stand <- lm(linkClicked_n ~ condition*knowledge_low, data = zdf)
summary(Link_Model_24_Stand)

# Use two tailed lm function to format
Link_Model_24_Results <- format_lm_bin_output_twotailed(Link_Model_24_robust, Link_Model_24_Stand)

# Outputs:
Link_Model_24_Results$appendix   

##

# High knowledge
Link_Model_25 <- lm(linkClicked_n ~ condition*knowledge_high, data = df)
summary(Link_Model_25) 

Link_Model_25_robust <- coeftest(Link_Model_25, vcov = vcovHC(Link_Model_25, type = "HC3"))
Link_Model_25_robust 

Link_Model_25_Stand <- lm(linkClicked_n ~ condition*knowledge_high, data = zdf)
summary(Link_Model_25_Stand)

# Use two tailed lm function to format
Link_Model_25_Results <- format_lm_bin_output_twotailed(Link_Model_25_robust, Link_Model_25_Stand)

# Outputs:
Link_Model_25_Results$appendix  

```

# By Region

```{r, Link Clicks Interaction with Region Two-Tailed}

# Interaction with region
Link_Model_26 <- lm(linkClicked_n ~ condition*region, data = df)
summary(Link_Model_26) 

# Means within each region
linkmeansregion <- emmeans(Link_Model_26, ~ condition | region, level = 0.95)

# Condition differences by region
linkcomparecond <- as.data.frame(pairs(linkmeansregion, adjust = "None", by = "region")) %>%
  filter(grepl("ControlCondition", contrast)) # Only keep comparisons with the control condition

linkcomparecond

# Apply formatting and sorting
linkcomparecond_clean <- linkcomparecond %>%
  mutate(
    Contrast = contrast,
    'PP Inc.' = sprintf("%.2f", (-100)*estimate), # Flip direction, flip intervention names in Latex
    b = sprintf("%.2f", (-1)*estimate),
    SE = sprintf("%.2f", SE),
    t = sprintf("%.2f", (-1)*t.ratio),
    p = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value))),
    p.value_two = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value)))) %>%
    dplyr::select(Contrast, 'PP Inc.', b, SE, t, p)

linkcomparecond_clean

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r", "r")

linkcomparecond_clean_appendix_xtable <- xtable(linkcomparecond_clean, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(linkcomparecond_clean_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# By Swing State

```{r, Link Clicks Interaction with Swing State}

# Interaction with swing state status
Link_Model_27 <- lm(linkClicked_n ~ condition*swing_E, data = df)
summary(Link_Model_27) 

Link_Model_27_robust <- coeftest(Link_Model_27, vcov = vcovHC(Link_Model_27, type = "HC3"))
Link_Model_27_robust 

Link_Model_27_Stand <- lm(linkClicked_n ~ condition*swing_E, data = zdf)
summary(Link_Model_27_Stand)

# Use two tailed lm function to format
Link_Model_27_Results <- format_lm_bin_output_twotailed(Link_Model_27_robust, Link_Model_27_Stand)

# Outputs:
Link_Model_27_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_27_Results$appendix_xtable, include.rownames = FALSE)

##

# Non-swing state

Link_Model_28 <- lm(linkClicked_n ~ condition*swing, data = df)
summary(Link_Model_28) 

Link_Model_28_robust <- coeftest(Link_Model_28, vcov = vcovHC(Link_Model_28, type = "HC3"))
Link_Model_28_robust 

Link_Model_28_Stand <- lm(linkClicked_n ~ condition*swing, data = zdf)
summary(Link_Model_28_Stand)

# Use two tailed lm function to format
Link_Model_28_Results <- format_lm_bin_output_twotailed(Link_Model_28_robust, Link_Model_28_Stand)

Link_Model_28_Results$appendix   # Cleaned and formatted for LaTeX

# Swing state

Link_Model_29 <- lm(linkClicked_n ~ condition*swing_r, data = df)
summary(Link_Model_29) 

Link_Model_29_robust <- coeftest(Link_Model_29, vcov = vcovHC(Link_Model_29, type = "HC3"))
Link_Model_29_robust 

Link_Model_29_Stand <- lm(linkClicked_n ~ condition*swing_r, data = zdf)
summary(Link_Model_29_Stand)

# Use two tailed lm function to format
Link_Model_29_Results <- format_lm_bin_output_twotailed(Link_Model_29_robust, Link_Model_29_Stand)

Link_Model_29_Results$appendix   # Cleaned and formatted for LaTeX

```

# Cost of Voting Index (COVI)

```{r, Link Clicks Interaction with COVI Two-Tailed}

# Test the interaction with COVI score
Link_Model_30 <- lm(linkClicked_n ~ condition*COVI_c, data = df)
summary(Link_Model_30) 

Link_Model_30_robust <- coeftest(Link_Model_30, vcov = vcovHC(Link_Model_30, type = "HC3"))
Link_Model_30_robust 

Link_Model_30_Stand <- lm(linkClicked_n ~ condition*COVI_c, data = zdf)
summary(Link_Model_30_Stand) 

# Use two tailed lm function to format
Link_Model_30_Results <- format_lm_bin_output_twotailed(Link_Model_30_robust, Link_Model_30_Stand)

# Outputs:
Link_Model_30_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Link_Model_30_Results$appendix_xtable, include.rownames = FALSE)

```

################################################################################################################
################################################# Registration ################################################# 
################################################################################################################

# OLS

```{r, Regisration One-Tailed (OLS)}

# Fit the model 
Registration_Model_1 <- lm(register_n ~ condition, data = df) 
summary(Registration_Model_1)

Registration_Model_1_robust <- coeftest(Registration_Model_1, vcov = vcovHC(Registration_Model_1, type = "HC3"))
Registration_Model_1_robust

Registration_Model_1_Stand <- lm(register_n ~ condition, data = zdf) 
summary(Registration_Model_1_Stand)

Registration_Model_1_Results <- format_lm_bin_output_onetailed(Registration_Model_1_robust, Registration_Model_1_Stand)

# Outputs:
Registration_Model_1_Results$appendix   # Cleaned and formatted for LaTex

# Go to BH section for Latex

# Plot percentages within each condition
Registration_Model_1_Results_plot <- as.data.frame(emmeans(Registration_Model_1, ~ condition, level = 0.90)) %>%
  rename(Condition = condition) %>%
    mutate(
    Mean = emmean*100,
    Lower_ci = lower.CL*100,
    Upper_ci = upper.CL*100
  ) %>%
dplyr::select(Condition, Mean, Lower_ci, Upper_ci) 

rownames(Registration_Model_1_Results_plot) <- NULL

Registration_Model_1_Results_plot

# Export the table as a data set 
# write.csv(Registration_Model_1_Results_plot, file = "Register_Percent.csv")

```

# Bayes

```{r, Regisration, Bayes}

df_bayes <- na.omit(df[, c("register_n", "condition")])

bf_anova <- anovaBF(register_n ~ condition, data = df_bayes)
bf_anova  

```

# Tukey - not needed becuase no intervention was successful

# OLS Among Compliers

```{r, Registration Among Compliers (Link Clickers)}

# Create a sample of only people who registered
df_click <- df %>%
  filter(linkClicked ==1)

nrow(df_click) # 352

zdf_click <- zdf %>%
  filter(linkClicked ==1)

nrow(zdf_click) # 352

# Fit the model 
Registration_Model_2 <- lm(register_n ~ condition, data = df_click)
summary(Registration_Model_2)

Registration_Model_2_robust <- coeftest(Registration_Model_2, vcov = vcovHC(Registration_Model_2, type = "HC3"))
Registration_Model_2_robust

Registration_Model_2_Stand <- lm(register_n ~ condition, data = zdf_click)
summary(Registration_Model_2_Stand)

# Use one tailed lm function to format
Registration_Model_2_Results <- format_lm_bin_output_onetailed(Registration_Model_2_robust, Registration_Model_2_Stand)

# Outputs:
Registration_Model_2_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_2_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

# (no int sig even for clickers)

```

# Logit

```{r, Regisration One-Tailed (Logit - Pre-registered)}

# Fit the model (use logit)
Registration_Model_3 <- glm(register ~ condition, data = df, family = binomial(link = "logit"))
summary(Registration_Model_3)

Registration_Model_3_robust <- coeftest(Registration_Model_3, vcov = vcovHC(Registration_Model_3, type = "HC3"))

# Use one tailed glm function to format
Registration_Model_3_Results <- format_logit_output_onetailed(Registration_Model_3_robust)

# Outputs:
Registration_Model_3_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_3_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Firth's Penalized Regression

```{r, Registration Firth's Robustness Check One-Tailed}

# Firth’s penalized logistic regression
Registration_Model_4 <- logistf(data=df, register~condition)
summary(Registration_Model_4)

# Extract coefficients, standard errors, p-values, and confidence intervals
coefs <- coef(Registration_Model_4)
se <- sqrt(diag(Registration_Model_4$var))
p_values <- (Registration_Model_4$prob)/2
conf_int <- confint(Registration_Model_4, level = .90)

# Create a data frame
Registration_Model_4_Results <- data.frame(
  Variable = gsub("condition", "", names(coefs)),
  Log_Odds = coefs,
  OR = exp(coefs),
  SE_LO = se,
  SE = exp(se),
  p = p_values,
  Lower_ci_LO = conf_int[, 1],
  Upper_ci_LO = conf_int[, 2],
  Lower_ci = exp(conf_int[, 1]),
  Upper_ci = exp(conf_int[, 2])
)

rownames(Registration_Model_4_Results) <- NULL

# Clean up
Registration_Model_4_Results <- Registration_Model_4_Results %>%
  mutate(
    Variable = dplyr::recode(Variable, !!!variable_labels), # Edit variable names
    Log_Odds = sprintf("%.2f", Log_Odds), # Round 
    OR = sprintf("%.2f", OR), 
    SE_LO = sprintf("%.2f", SE_LO),
    SE = sprintf("%.2f", SE),
    p = ifelse(p < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p))), 
    Lower_ci_LO = sprintf("%.2f", Lower_ci_LO), # CI in brackets
    Upper_ci_LO = sprintf("%.2f", Upper_ci_LO),
    `90% CI` = paste0("[", Lower_ci_LO, ", ", Upper_ci_LO, "]"),
    Lower_ci = sprintf("%.2f", Lower_ci), 
    Upper_ci = sprintf("%.2f", Upper_ci),
    `90% CI` = paste0("[", Lower_ci, ", ", Upper_ci, "]")
        
) %>%
    dplyr::select(Variable,
         OR, SE, p, `90% CI`)

Registration_Model_4_Results

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r")
Registration_Model_4_Results_appendix_xtable <- xtable(Registration_Model_4_Results, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(Registration_Model_4_Results_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Mixed Model Accounting for Within-state Non-independence

```{r, Registration with Covariates MLM Robustness Check One-Tailed}

# Fit the model
Regitration_Model_5 <- lmer(register_n ~ condition + (1 | state), data = df)
summary(Regitration_Model_5)

Regitration_Model_5_Stand <- lmer(register_n ~ condition + (1 | state), data = zdf)
summary(Regitration_Model_5_Stand)

# Use one tailed glm MLM function to format 
Regitration_Model_5_Results <- format_linear_mixed_bin_output_onetailed(Regitration_Model_5, Regitration_Model_5_Stand)

# Outputs:
Regitration_Model_5_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Regitration_Model_5_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# OLS with Covariates

```{r, Registration with Covariates One-Tailed}

# Fit the model 
Registration_Model_6 <- lm(register_n ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = df) 
summary(Registration_Model_6)

Registration_Model_6_robust <- coeftest(Registration_Model_6, vcov = vcovHC(Registration_Model_6, type = "HC3"))

Registration_Model_6_Stand <- lm(register_n ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = zdf) 
summary(Registration_Model_6_Stand)

# Use one tailed glm function to format
Registration_Model_6_Results <- format_lm_bin_output_onetailed(Registration_Model_6_robust, Registration_Model_6_Stand)

# Outputs:
Registration_Model_6_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_6_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Logit with Covariates (Pre-registered)

```{r, Link Click One-Tailed with Covariates}

# Fit the model (use logit)
Registration_Model_7 <- glm(register ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = df, family = binomial(link = "logit")) 
summary(Registration_Model_7)

Registration_Model_7_robust <- coeftest(Registration_Model_7, vcov = vcovHC(Registration_Model_7, type = "HC3"))

# Use one tailed glm function to format
Registration_Model_7_Results <- format_logit_output_onetailed(Registration_Model_7_robust)

# Outputs:
Registration_Model_7_Results$appendix   

print.xtable(Registration_Model_7_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# OLS - All Legs

```{r, Registration All Legs One-Tailed}

# Fit the model (use OLS)
Registration_Model_7 <- lm(register_n ~ condition_binary, data = df) 
summary(Registration_Model_7)

Registration_Model_7_robust <- coeftest(Registration_Model_7, vcov = vcovHC(Registration_Model_7, type = "HC3"))

Registration_Model_7_Stand <- lm(register_n ~ condition_binary, data = zdf) 
summary(Registration_Model_7_Stand)

# Use one tailed lm function to format
Registration_Model_7_Results <- format_lm_bin_output_onetailed(Registration_Model_7_robust, Registration_Model_7_Stand)

# Outputs:
Registration_Model_7_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_7_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

############# Actual Registration Moderations (two-tailed)

# Demographics

```{r, Registration Interaction with Ideology Two-Tailed}

# Test the interaction with ideology
Registration_Model_7 <- lm(register_n ~ condition*ide_c, data = df)
summary(Registration_Model_7) 

Registration_Model_7_robust <- coeftest(Registration_Model_7, vcov = vcovHC(Registration_Model_7, type = "HC3"))
Registration_Model_7_robust 

Registration_Model_7_Stand <- lm(register_n ~ condition*ide_c, data = zdf)
summary(Registration_Model_7_Stand) 

# Use two tailed lm function to format
Registration_Model_7_Results <- format_lm_bin_output_twotailed(Registration_Model_7_robust, Registration_Model_7_Stand)

# Outputs:
Registration_Model_7_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_7_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Registration Interaction with Gender Two-Tailed}

# Condition*gender
Registration_Model_8 <- lm(register_n ~ condition*gend_e, data = df)
summary(Registration_Model_8) 

Registration_Model_8_robust <- coeftest(Registration_Model_8, vcov = vcovHC(Registration_Model_8, type = "HC3"))
Registration_Model_8_robust 

Registration_Model_8_Stand <- lm(register_n ~ condition*gend_e, data = zdf)
summary(Registration_Model_8_Stand) 

# Use two tailed lm function to format
Registration_Model_8_Results <- format_lm_bin_output_twotailed(Registration_Model_8_robust, Registration_Model_8_Stand)

# Outputs:
Registration_Model_8_Results$appendix # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_8_Results$appendix_xtable, include.rownames = FALSE) 

```

```{r, Registration Interaction with Race Two-Tailed}

# Condition*race
Registration_Model_9 <- lm(register_n ~ condition*race_bin_e, data = df)
summary(Registration_Model_9) 

Registration_Model_9_robust <- coeftest(Registration_Model_9, vcov = vcovHC(Registration_Model_9, type = "HC3"))
Registration_Model_9_robust

Registration_Model_9_Stand <- glm(register_n ~ condition*race_bin_e, data = zdf)
summary(Registration_Model_9_Stand) 

# Use two tailed lm function to format
Registration_Model_9_Results <- format_lm_bin_output_twotailed(Registration_Model_9_robust, Registration_Model_9_Stand)

# Outputs:
Registration_Model_9_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_9_Results$appendix_xtable, include.rownames = FALSE, longtable = TRUE) # Syntax for latex editor

##

# White participants 

Registration_Model_10 <- lm(register_n ~ condition*race_bin, data = df)
summary(Registration_Model_10) 

Registration_Model_10_robust <- coeftest(Registration_Model_10, vcov = vcovHC(Registration_Model_10, type = "HC3"))
Registration_Model_10_robust

Registration_Model_10_Stand <- lm(register_n ~ condition*race_bin, data = zdf)
summary(Registration_Model_10_Stand) 

# Use two tailed lm function to format
Registration_Model_10_Results <- format_lm_bin_output_twotailed(Registration_Model_10_robust, Registration_Model_10_Stand)

# Outputs:
Registration_Model_10_Results$appendix 

##

# Non-White participants 

Registration_Model_11 <- lm(register_n ~ condition*race_bin_r, data = df)
summary(Registration_Model_11) 

Registration_Model_11_robust <- coeftest(Registration_Model_11, vcov = vcovHC(Registration_Model_11, type = "HC3"))
Registration_Model_11_robust

Registration_Model_11_Stand <- lm(register_n ~ condition*race_bin_r, data = zdf)
summary(Registration_Model_11_Stand) 

# Use two tailed lm function to format
Registration_Model_11_Results <- format_lm_bin_output_twotailed(Registration_Model_11_robust, Registration_Model_11_Stand)

# Outputs:
Registration_Model_11_Results$appendix

```

```{r, Registration Interaction with Age Two-Tailed}

# Condition*age
Registration_Model_12 <- lm(register_n ~ condition*age_c, data = df)
summary(Registration_Model_12) 

Registration_Model_12_robust <- coeftest(Registration_Model_12, vcov = vcovHC(Registration_Model_12, type = "HC3"))
Registration_Model_12_robust 

Registration_Model_12_Stand <- lm(register_n ~ condition*age_c, data = zdf)
summary(Registration_Model_12_Stand) 

# Use two tailed lm function to format
Registration_Model_12_Results <- format_lm_bin_output_twotailed(Registration_Model_12_robust, Registration_Model_12_Stand)

# Outputs:
Registration_Model_12_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_12_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Registration Interaction with Income Two-Tailed}

# Condition*income
Registration_Model_13 <- lm(register_n ~ condition*income_c, data = df)
summary(Registration_Model_13) 

Registration_Model_13_robust <- coeftest(Registration_Model_13, vcov = vcovHC(Registration_Model_13, type = "HC3"))
Registration_Model_13_robust 

Registration_Model_13_Stand <- lm(register_n ~ condition*income_c, data = zdf)
summary(Registration_Model_13_Stand) 

# Use two tailed lm function to format
Registration_Model_13_Results <- format_lm_bin_output_twotailed(Registration_Model_13_robust, Registration_Model_13_Stand)

# Outputs:
Registration_Model_13_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_13_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

##

# Low income

Registration_Model_14 <- lm(register_n ~ condition*income_low, data = df)
summary(Registration_Model_14) 

Registration_Model_14_robust <- coeftest(Registration_Model_14, vcov = vcovHC(Registration_Model_14, type = "HC3"))
Registration_Model_14_robust 

Registration_Model_14_Stand <- lm(register_n ~ condition*income_low, data = zdf)
summary(Registration_Model_14_Stand) 

# Use two two tailed lm function to format
Registration_Model_14_Results <- format_lm_bin_output_twotailed(Registration_Model_14_robust, Registration_Model_14_Stand)

# Outputs:
Registration_Model_14_Results$appendix 

##

# High income

Registration_Model_15 <- lm(register_n ~ condition*income_high, data = df)
summary(Registration_Model_15) 

Registration_Model_15_robust <- coeftest(Registration_Model_15, vcov = vcovHC(Registration_Model_15, type = "HC3"))
Registration_Model_15_robust 

Registration_Model_15_Stand <- lm(register_n ~ condition*income_high, data = zdf)
summary(Registration_Model_15_Stand) 

# Use two tailed lm function to format
Registration_Model_15_Results <- format_lm_bin_output_twotailed(Registration_Model_15_robust, Registration_Model_15_Stand)

# Outputs:
Registration_Model_15_Results$appendix 

```

```{r, Registration Interaction with Education Two-Tailed}

# Condition*education
Registration_Model_16 <- lm(register_n ~ condition*edu_c, data = df)
summary(Registration_Model_16) 

Registration_Model_16_robust <- coeftest(Registration_Model_16, vcov = vcovHC(Registration_Model_16, type = "HC3"))
Registration_Model_16_robust 

Registration_Model_16_Stand <- lm(register_n ~ condition*edu_c, data = zdf)
summary(Registration_Model_16_Stand) 

# Use two tailed lm function to format
Registration_Model_16_Results <- format_lm_bin_output_twotailed(Registration_Model_16_robust, Registration_Model_16_Stand)

# Outputs:
Registration_Model_16_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_16_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Pre-Intention to Register

```{r, Registration Interaction with Pre-Intention to Register Two-Tailed}

# Test the interaction with pre-intention to register
Registration_Model_17 <- lm(register_n ~ condition*pre_intention_c, data = df)
summary(Registration_Model_17) 

Registration_Model_17_robust <- coeftest(Registration_Model_17, vcov = vcovHC(Registration_Model_17, type = "HC3"))
Registration_Model_17_robust 

Registration_Model_17_Stand <- lm(register_n ~ condition*pre_intention_c, data = zdf)
summary(Registration_Model_17_Stand) 

# Use two tailed lm function to format
Registration_Model_17_Results <- format_lm_bin_output_twotailed(Registration_Model_17_robust, Registration_Model_17_Stand)

# Outputs:
Registration_Model_17_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_17_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Interest

```{r, Registration Interaction with Interest Two-Tailed}

# Test the interaction with interest
Registration_Model_18 <- lm(register_n ~ condition*interest_c, data = df)
summary(Registration_Model_18) 

Registration_Model_18_robust <- coeftest(Registration_Model_18, vcov = vcovHC(Registration_Model_18, type = "HC3"))
Registration_Model_18_robust 

Registration_Model_18_Stand <- lm(register_n ~ condition*interest_c, data = zdf)
summary(Registration_Model_18_Stand) 

# Use two tailed glm function to format
Registration_Model_18_Results <- format_lm_bin_output_twotailed(Registration_Model_18_robust, Registration_Model_18_Stand)

# Outputs:
Registration_Model_18_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_18_Results$appendix_xtable, include.rownames = FALSE)

```

# Knowledge

```{r, Registration Interaction with Knowledge Two-Tailed}

# Test the interaction with knowledge
Registration_Model_19 <- lm(register_n ~ condition*knowledge_c, data = df)
summary(Registration_Model_19) 

Registration_Model_19_robust <- coeftest(Registration_Model_19, vcov = vcovHC(Registration_Model_19, type = "HC3"))
Registration_Model_19_robust 

Registration_Model_19_Stand <- lm(register_n ~ condition*knowledge_c, data = zdf)
summary(Registration_Model_19_Stand) 

# Use two tailed lm function to format
Registration_Model_19_Results <- format_lm_bin_output_twotailed(Registration_Model_19_robust, Registration_Model_19_Stand)

# Outputs:
Registration_Model_19_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_19_Results$appendix_xtable, include.rownames = FALSE)

```

# By Region

```{r, Registration Interaction with Region Two-Tailed}

# Interaction with region
Registration_Model_20 <- lm(register_n ~ condition*region, data = df)
summary(Registration_Model_20) 

# Means within each region
regmeansregion <- emmeans(Registration_Model_20, ~ condition | region, level = 0.95)

# Condition differences by region
regcomparecond <- as.data.frame(pairs(regmeansregion, adjust = "None", by = "region")) %>%
  filter(grepl("ControlCondition", contrast)) # Only keep comparisons with the control condition

regcomparecond

# Apply formatting and sorting
regcomparecond_clean <- regcomparecond %>%
  mutate(
    Contrast = contrast,
    'PP Inc.' = sprintf("%.2f", -100*estimate),
    b = sprintf("%.2f", -1*estimate),
    SE = sprintf("%.2f", SE),
    t = sprintf("%.2f", -1*t.ratio),
    p = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value))),
    p.value_two = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value)))) %>%
    dplyr::select(Contrast, 'PP Inc.', b, SE, t, p)

regcomparecond_clean

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r", "r")

regcomparecond_clean_appendix_xtable <- xtable(regcomparecond_clean, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(regcomparecond_clean_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# By Swing State

```{r, Registration Interaction with Swing State}

# Interaction with swing state status
Registration_Model_21 <- lm(register_n ~ condition*swing_E, data = df)
summary(Registration_Model_21) 

Registration_Model_21_robust <- coeftest(Registration_Model_21, vcov = vcovHC(Registration_Model_21, type = "HC3"))
Registration_Model_21_robust 

Registration_Model_21_Stand <- lm(register_n ~ condition*swing_E, data = zdf)
summary(Registration_Model_21_Stand)

# Use two tailed lm function to format
Registration_Model_21_Results <- format_lm_bin_output_twotailed(Registration_Model_21_robust, Registration_Model_21_Stand)

# Outputs:
Registration_Model_21_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_21_Results$appendix_xtable, include.rownames = FALSE)

```

# Cost of Voting Index (COVI)

```{r, Registration Interaction with COVI Two-Tailed}

# Test the interaction with COVI score
Registration_Model_24 <- lm(register_n ~ condition*COVI_c, data = df)
summary(Registration_Model_24) 

Registration_Model_24_robust <- coeftest(Registration_Model_24, vcov = vcovHC(Registration_Model_24, type = "HC3"))
Registration_Model_24_robust 

Registration_Model_24_Stand <- lm(register_n ~ condition*COVI_c, data = zdf)
summary(Registration_Model_24_Stand) 

# Use two tailed lm function to format
Registration_Model_24_Results <- format_lm_bin_output_twotailed(Registration_Model_24_robust, Registration_Model_24_Stand)

# Outputs:
Registration_Model_24_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_24_Results$appendix_xtable, include.rownames = FALSE)

```

# Time Between Participation and Registration

```{r, Link Clicks Interaction with Time Two-Tailed}

Registration_Model_25 <- lm(days_between ~ condition, data = df)
summary(Registration_Model_25) 

Registration_Model_25_robust <- coeftest(Registration_Model_25, vcov = vcovHC(Registration_Model_25, type = "HC3"))
Registration_Model_25_robust

Registration_Model_25_Stand <- lm(days_between ~ condition, data = zdf)
summary(Registration_Model_25_Stand) 

# Use two tailed lm function to format
Registration_Model_25_Results <- format_lm_output_twotailed(Registration_Model_25_robust, Registration_Model_25_Stand)

# Outputs:
Registration_Model_25_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Registration_Model_25_Results$appendix_xtable, include.rownames = FALSE)

# (nothing worth interpreting given how few people registered within each cond)

```

################################################################################################################
################################################ BH Adjustments ################################################
################################################################################################################

```{r, BH Adjustments}

# Use for link clicks, registration, and intentions only, since that is what we pre-registered

# Pull p-values
pvals_link <- Link_Model_1_Results$full$p[2:11]
pvals_int <- Intentions_Model_1_Results$full$p[2:11]
pvals_reg <- Registration_Model_1_Results$full$p[2:11]

# Combine p-values and apply BH correction
all_condition_pvals <- c(pvals_link, pvals_int, pvals_reg)
adjusted_pvals <- p.adjust(all_condition_pvals, method = "BH")

# Split again
adj_link <- adjusted_pvals[1:10] 
adj_int  <- adjusted_pvals[11:20]
adj_reg  <- adjusted_pvals[21:30]

# Reassign to each model and print for appendix

# Link clicks 
Link_Model_1_Results$full$p_BH <- NA
Link_Model_1_Results$full$p_BH[2:11] <- adj_link

Link_Model_1_Results$appendix$p_BH <- NA
Link_Model_1_Results$appendix$p_BH[2:11] <- adj_link

Link_Model_1_Results$appendix <- Link_Model_1_Results$appendix %>%
   mutate(p_BH = ifelse(p_BH < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p_BH))))

Link_Model_1_Results$appendix 

align_spec <- c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r")
  
Link_Model_1_Results_xtable <- xtable(Link_Model_1_Results$appendix, align = align_spec, booktabs = T)

colnames(Link_Model_1_Results_xtable)[colnames(Link_Model_1_Results_xtable) == "p_BH"] <- "p (BH)"
  
# Print appendix
print.xtable(Link_Model_1_Results_xtable, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

##

# Voting intentions
Intentions_Model_1_Results$full$p_BH <- NA
Intentions_Model_1_Results$full$p_BH[2:11] <- adj_int

Intentions_Model_1_Results$appendix$p_BH <- NA
Intentions_Model_1_Results$appendix$p_BH[2:11] <- adj_int

Intentions_Model_1_Results$appendix <- Intentions_Model_1_Results$appendix %>%
   mutate(p_BH = ifelse(p_BH < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p_BH))))

Intentions_Model_1_Results$appendix

align_spec <- c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r")

Intentions_Model_1_Results_xtable <- xtable(Intentions_Model_1_Results$appendix, align = align_spec, booktabs = T)

colnames(Intentions_Model_1_Results_xtable)[colnames(Intentions_Model_1_Results_xtable) == "p_BH"] <- "p (BH)"
  
# Print appendix
print.xtable(Intentions_Model_1_Results_xtable, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

##

# Registration
Registration_Model_1_Results$full$p_BH <- NA
Registration_Model_1_Results$full$p_BH[2:11] <- adj_reg

Registration_Model_1_Results$appendix$p_BH <- NA
Registration_Model_1_Results$appendix$p_BH[2:11] <- adj_reg

Registration_Model_1_Results$appendix <- Registration_Model_1_Results$appendix %>%
   mutate(p_BH = ifelse(p_BH < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p_BH))))

Registration_Model_1_Results$appendix

align_spec <- c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r")
  
Registration_Model_1_Results_xtable <- xtable(Registration_Model_1_Results$appendix, align = align_spec, booktabs = T)

colnames(Registration_Model_1_Results_xtable)[colnames(Registration_Model_1_Results_xtable) == "p_BH"] <- "p (BH)"
  
# Print appendix
print.xtable(Registration_Model_1_Results_xtable, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

```

```{r, BH Adjustments - Covariates}

# Use for link clicks, registration, and intentions only, since that is what we pre-registered

# Pull p-values
pvals_link <- Link_Model_5_Results$full$p[2:11]
pvals_int <- Intentions_Model_3_Results$full$p[2:11]
pvals_reg <- Registration_Model_6_Results$full$p[2:11]

# Combine p-values and apply BH correction
all_condition_pvals <- c(pvals_link, pvals_int, pvals_reg)
adjusted_pvals <- p.adjust(all_condition_pvals, method = "BH")

# Split again
adj_link <- adjusted_pvals[1:10] 
adj_int  <- adjusted_pvals[11:20]
adj_reg  <- adjusted_pvals[21:30]

# Reassign to each model and print for appendix

# Link clicks 
Link_Model_5_Results$full$p_BH <- NA
Link_Model_5_Results$full$p_BH[2:11] <- adj_link

Link_Model_5_Results$appendix$p_BH <- NA
Link_Model_5_Results$appendix$p_BH[2:11] <- adj_link

Link_Model_5_Results$appendix <- Link_Model_5_Results$appendix %>%
   mutate(p_BH = ifelse(p_BH < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p_BH))))

Link_Model_5_Results$appendix 

align_spec <- c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r")
  
Link_Model_5_Results_xtable <- xtable(Link_Model_5_Results$appendix, align = align_spec, booktabs = T)

colnames(Link_Model_5_Results_xtable)[colnames(Link_Model_5_Results_xtable) == "p_BH"] <- "p (BH)"
  
# Print appendix
print.xtable(Link_Model_5_Results_xtable, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

##

# Voting intentions
Intentions_Model_3_Results$full$p_BH <- NA
Intentions_Model_3_Results$full$p_BH[2:11] <- adj_int

Intentions_Model_3_Results$appendix$p_BH <- NA
Intentions_Model_3_Results$appendix$p_BH[2:11] <- adj_int

Intentions_Model_3_Results$appendix <- Intentions_Model_3_Results$appendix %>%
   mutate(p_BH = ifelse(p_BH < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p_BH))))

Intentions_Model_3_Results$appendix

align_spec <- c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r")

Intentions_Model_3_Results_xtable <- xtable(Intentions_Model_3_Results$appendix, align = align_spec, booktabs = T)

colnames(Intentions_Model_3_Results_xtable)[colnames(Intentions_Model_3_Results_xtable) == "p_BH"] <- "p (BH)"
  
# Print appendix
print.xtable(Intentions_Model_3_Results_xtable, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

##

# Registration
Registration_Model_6_Results$full$p_BH <- NA
Registration_Model_6_Results$full$p_BH[2:11] <- adj_reg

Registration_Model_6_Results$appendix$p_BH <- NA
Registration_Model_6_Results$appendix$p_BH[2:11] <- adj_reg

Registration_Model_6_Results$appendix <- Registration_Model_6_Results$appendix %>%
   mutate(p_BH = ifelse(p_BH < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p_BH))))

Registration_Model_6_Results$appendix

align_spec <- c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r")
  
Registration_Model_6_Results_xtable <- xtable(Registration_Model_6_Results$appendix, align = align_spec, booktabs = T)

colnames(Registration_Model_6_Results_xtable)[colnames(Registration_Model_6_Results_xtable) == "p_BH"] <- "p (BH)"
  
# Print appendix
print.xtable(Registration_Model_6_Results_xtable, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

```

################################################################################################################
########################################## Actual Voting (Exploratory) #########################################
################################################################################################################

# OLS

```{r, Voting One-Tailed OLS}

# Fit the model 
Vote_Model_1 <- lm(vote_n ~ condition, data = df) 
summary(Vote_Model_1)

Vote_Model_1_robust <- coeftest(Vote_Model_1, vcov = vcovHC(Vote_Model_1, type = "HC3"))

Vote_Model_1_Stand <- lm(vote_n ~ condition, data = zdf) 
summary(Vote_Model_1_Stand)

# Use one tailed lm function to format
Vote_Model_1_Results <- format_lm_bin_output_onetailed(Vote_Model_1_robust, Vote_Model_1_Stand)

# Outputs:
Vote_Model_1_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_1_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

# Plot percentages within each condition
Vote_Model_1_Results_plot <- as.data.frame(emmeans(Vote_Model_1, ~ condition, level = 0.90)) %>%
  rename(Condition = condition) %>%
    mutate(
    Mean = emmean*100,
    Lower_ci = lower.CL*100,
    Upper_ci = upper.CL*100
  ) %>%
dplyr::select(Condition, Mean, Lower_ci, Upper_ci) 

rownames(Vote_Model_1_Results_plot) <- NULL

Vote_Model_1_Results_plot

# write.csv(Vote_Model_1_Results_plot, file = "Vote_Percent.csv")

```

# OLS Among Registered

```{r, Voting One-Tailed Among Registered (OLS)}

# Create sample of only people who registered
df_register <- df %>%
  filter(register ==1)

nrow(df_register) # 380

zdf_register <- zdf %>%
  filter(register == 1)

nrow(zdf_register) # 380

# Fit the model 
Vote_Model_2 <- lm(vote_n ~ condition, data = df_register) 
summary(Vote_Model_2)

Vote_Model_2_Stand <- lm(vote_n ~ condition, data = zdf_register) 
summary(Vote_Model_2_Stand) # Don't use standardized, small sample size & base-rate makes it such that estimates are very large

# Not powered enough to do robust model 

Vote_Model_2_clean <- broom::tidy(Vote_Model_2, conf.int = TRUE, conf.level = 0.90)
Vote_Model_2_clean

Vote_Model_2_Stand_clean <- broom::tidy(Vote_Model_2_Stand, conf.int = TRUE, conf.level = 0.90)
Vote_Model_2_Stand_clean

# Create data frame
Vote_Model_2_Results_df <- data.frame(
  Condition = Vote_Model_2_clean$term,
  b = Vote_Model_2_clean$estimate,
  SE = Vote_Model_2_clean$std.error,
  t = Vote_Model_2_clean$statistic,
  p = Vote_Model_2_clean$p.value / 2,  # One-tailed
  Lower_ci = Vote_Model_2_clean$conf.low,
  Upper_ci = Vote_Model_2_clean$conf.high
  ) %>%
  mutate(
  Condition = gsub('condition', "", Vote_Model_2_clean$term))

Vote_Model_2_Results_df

# Apply shrinkage 
Vote_Model_2_shrunk_df <- shrink_condition_effects(Vote_Model_2, prefix = 'condition')
Vote_Model_2_Results_df <- left_join(Vote_Model_2_Results_df, Vote_Model_2_shrunk_df, by = "Condition") %>%
  dplyr::select(-Original)

Vote_Model_2_Results_df

# Full data frame 
Vote_Model_2_Results_df_full <- Vote_Model_2_Results_df

Vote_Model_2_Results_appendix <- Vote_Model_2_Results_df_full %>%
  mutate(
    Variable = dplyr::recode(Condition, !!!variable_labels), # Edit variable names
    'PP Inc.' = clean_round(b*100), 
    b = clean_round(b), 
    SE = clean_round(SE),
    t = clean_round(t),
    p = ifelse(p < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p))), 
    Shrunk = ifelse(is.na(Shrunk), "", sprintf("%.2f", Shrunk)),
    Lower_ci = clean_round(Lower_ci), # CI in brackets
    Upper_ci = clean_round(Upper_ci),
    `90% CI` = paste0("[", Lower_ci, ", ", Upper_ci, "]")
) %>%
    dplyr::select(Variable,
           'PP Inc.', b, SE, t, p, Shrunk,
           `90% CI`)

Vote_Model_2_Results_appendix

# Syntax for latex editor
align_spec <- c("l","l", "r", "r", "r", "r", "r", "r", "r")

Vote_Model_2_Results_appendix_xtable <- xtable(Vote_Model_2_Results_appendix, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(Vote_Model_2_Results_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

# (nothing sig)

```

# Logit

```{r, Voting One-Tailed (logit)}

# Fit the model 
Vote_Model_3 <- glm(vote ~ condition, data = df, family = binomial(link = "logit")) 
summary(Vote_Model_3)

Vote_Model_3_robust <- coeftest(Vote_Model_3, vcov = vcovHC(Vote_Model_3, type = "HC3"))
Vote_Model_3_robust 

# Use one tailed glm function to format
Vote_Model_3_Results <- format_logit_output_onetailed(Vote_Model_3_robust)  

# Outputs:
Vote_Model_3_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_3_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Tukey - not needed becuase no intervention was successful

# Firth's Penalized Regression

```{r, Voting Firth's Robustness Check One-Tailed}

# Firth’s penalized logistic regression reduces bias in logistic regression with imbalanced data (i.e., more 0s than 1s)
Vote_Model_4 <- logistf(data=df, vote~condition)
summary(Vote_Model_4)

# Extract coefficients, standard errors, p-values, and confidence intervals
coefs <- coef(Vote_Model_4)
se <- sqrt(diag(Vote_Model_4$var))
p_values <- (Vote_Model_4$prob)/2
conf_int <- confint(Vote_Model_4, level = .90)

# Create a data frame
Vote_Model_4_Results <- data.frame(
  Variable = gsub("condition", "", names(coefs)),
  Log_Odds = coefs,
  OR = exp(coefs),
  SE_LO = se,
  SE = exp(se),
  p = p_values,
  Lower_ci_LO = conf_int[, 1],
  Upper_ci_LO = conf_int[, 2],
  Lower_ci = exp(conf_int[, 1]),
  Upper_ci = exp(conf_int[, 2])
)

rownames(Vote_Model_4_Results) <- NULL

Vote_Model_4_Results

# Clean up
Vote_Model_4_Results <- Vote_Model_4_Results %>%
  mutate(
    Variable = dplyr::recode(Variable, !!!variable_labels), # Edit variable names
    Log_Odds = sprintf("%.2f", Log_Odds), # Round 
    OR = sprintf("%.2f", OR), 
    SE_LO = sprintf("%.2f", SE_LO),
    SE = sprintf("%.2f", SE),
    p = ifelse(p < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p))), 
    Lower_ci_LO = sprintf("%.2f", Lower_ci_LO), # CI in brackets
    Upper_ci_LO = sprintf("%.2f", Upper_ci_LO),
    `90% CI` = paste0("[", Lower_ci_LO, ", ", Upper_ci_LO, "]"),
    Lower_ci = sprintf("%.2f", Lower_ci), 
    Upper_ci = sprintf("%.2f", Upper_ci),
    `90% CI` = paste0("[", Lower_ci, ", ", Upper_ci, "]")
        
) %>%
    dplyr::select(Variable,
         OR, SE, p, `90% CI`)

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r")

Vote_Model_4_Results_appendix_xtable <- xtable(Vote_Model_4_Results, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(Vote_Model_4_Results_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Mixed Model Accounting for Within-state Non-independence

```{r, Voting MLM Robustness Check One-Tailed}

# Fit the model
Vote_Model_5 <- lmer(vote_n ~ condition + (1 | state), data = df)
summary(Vote_Model_5)

Vote_Model_5_Stand <- lmer(vote_n ~ condition + (1 | state), data = zdf)
summary(Vote_Model_5_Stand)

# Use one tailed lm MLM function to format 
Vote_Model_5_Results <- format_linear_mixed_bin_output_onetailed(Vote_Model_5, Vote_Model_5_Stand)

# Outputs:
Vote_Model_5_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_5_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# With Covariates

```{r, Voting with Covariates One-Tailed (OLS)}

# Fit the model 
Vote_Model_6 <- lm(vote_n ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = df) 
summary(Vote_Model_6)

Vote_Model_6_robust <- coeftest(Vote_Model_6, vcov = vcovHC(Vote_Model_6, type = "HC3"))
Vote_Model_6_robust 

Vote_Model_6_Stand <- lm(vote_n ~ condition + pre_intention_c + gend_e + Asian_E + Black_E + Latinx_E + ME_E + Native_E + Multiracial_E + Other_E + age_c + income_c + edu_c, data = zdf) 
summary(Vote_Model_6_Stand)

# Use one tailed lm function to format
Vote_Model_6_Results <- format_lm_bin_output_onetailed(Vote_Model_6_robust, Vote_Model_6_Stand)  

# Outputs:
Vote_Model_6_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_6_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# OLS - All Legs

```{r, Voting All Legs One-Tailed}

# Fit the model (use OLS)
Vote_Model_7 <- lm(vote_n ~ condition_binary, data = df) 
summary(Vote_Model_7)

Vote_Model_7_robust <- coeftest(Vote_Model_7, vcov = vcovHC(Vote_Model_7, type = "HC3"))

Vote_Model_7_Stand <- lm(vote_n ~ condition_binary, data = zdf) 
summary(Vote_Model_7_Stand)

# Use one tailed lm function to format
Vote_Model_7_Results <- format_lm_bin_output_onetailed(Vote_Model_7_robust, Vote_Model_7_Stand)

# Outputs:
Vote_Model_7_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_7_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```


############# Voting Moderations (two-tailed)

# Demographics

```{r, Voting Interaction with Ideology Two-Tailed}

# Test the interaction with ideology
Vote_Model_7 <- lm(vote_n ~ condition*ide_c, data = df)
summary(Vote_Model_7) 

Vote_Model_7_robust <- coeftest(Vote_Model_7, vcov = vcovHC(Vote_Model_7, type = "HC3"))
Vote_Model_7_robust 

Vote_Model_7_Stand <- lm(vote_n ~ condition*ide_c, data = zdf)
summary(Vote_Model_7_Stand) 

# Use two tailed lm function to format
Vote_Model_7_Results <- format_lm_bin_output_twotailed(Vote_Model_7_robust, Vote_Model_7_Stand)

# Outputs:
Vote_Model_7_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_7_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Voting Interaction with Gender Two-Tailed}

# Condition*gender
Vote_Model_8 <- lm(vote_n ~ condition*gend_e, data = df)
summary(Vote_Model_8) 

Vote_Model_8_robust <- coeftest(Vote_Model_8, vcov = vcovHC(Vote_Model_8, type = "HC3"))
Vote_Model_8_robust 

Vote_Model_8_Stand <- lm(vote_n ~ condition*gend_e, data = zdf)
summary(Vote_Model_8_Stand) 

# Use two tailed lm function to format
Vote_Model_8_Results <- format_lm_bin_output_twotailed(Vote_Model_8_robust, Vote_Model_8_Stand)

# Outputs:
Vote_Model_8_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_8_Results$appendix_xtable, include.rownames = FALSE) 

##

# Men

Vote_Model_9 <- lm(vote_n ~ condition*gend_bin, data = df)
summary(Vote_Model_9) 

Vote_Model_9_robust <- coeftest(Vote_Model_9, vcov = vcovHC(Vote_Model_9, type = "HC3"))
Vote_Model_9_robust 

Vote_Model_9_Stand <- lm(vote_n ~ condition*gend_bin, data = zdf)
summary(Vote_Model_9_Stand) 

# Use two tailed lm function to format
Vote_Model_9_Results <- format_lm_bin_output_twotailed(Vote_Model_9_robust, Vote_Model_9_Stand)

# Outputs:
Vote_Model_9_Results$appendix      # Cleaned and formatted for LaTeX

##

# Women

Vote_Model_10 <- lm(vote_n ~ condition*gend_bin_r, data = df)
summary(Vote_Model_10) 

Vote_Model_10_robust <- coeftest(Vote_Model_10, vcov = vcovHC(Vote_Model_10, type = "HC3"))
Vote_Model_10_robust 

Vote_Model_10_Stand <- lm(vote_n ~ condition*gend_bin_r, data = zdf)
summary(Vote_Model_10_Stand) 

# Use two tailed lm function to format
Vote_Model_10_Results <- format_lm_bin_output_twotailed(Vote_Model_10_robust, Vote_Model_10_Stand)

# Outputs:
Vote_Model_10_Results$appendix   

```

```{r, Voting Interaction with Race Two-Tailed}

# Condition*race
Vote_Model_11 <- lm(vote_n ~ condition*race_bin_e, data = df)
summary(Vote_Model_11) 

Vote_Model_11_robust <- coeftest(Vote_Model_11, vcov = vcovHC(Vote_Model_11, type = "HC3"))
Vote_Model_11_robust 

Vote_Model_11_Stand <- lm(vote_n ~ condition*race_bin_e, data = zdf)
summary(Vote_Model_11_Stand) 

# Use two tailed glm function to format
Vote_Model_11_Results <- format_lm_bin_output_twotailed(Vote_Model_11_robust, Vote_Model_11_Stand)

# Outputs:
Vote_Model_11_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_11_Results$appendix_xtable, include.rownames = FALSE, longtable = TRUE) # Syntax for latex editor

```

```{r, Voting Interaction with Age Two-Tailed}

# Condition*age
Vote_Model_12 <- lm(vote_n ~ condition*age_c, data = df)
summary(Vote_Model_12) 

Vote_Model_12_robust <- coeftest(Vote_Model_12, vcov = vcovHC(Vote_Model_12, type = "HC3"))
Vote_Model_12_robust 

Vote_Model_12_Stand <- lm(vote_n ~ condition*age_c, data = zdf)
summary(Vote_Model_12_Stand) 

# Use two tailed lm function to format
Vote_Model_12_Results <- format_lm_bin_output_twotailed(Vote_Model_12_robust, Vote_Model_12_Stand)

# Outputs:
Vote_Model_12_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_12_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

```{r, Voting Interaction with Income Two-Tailed}

# Condition*income
Vote_Model_13 <- lm(vote_n ~ condition*income_c, data = df)
summary(Vote_Model_13) 

Vote_Model_13_robust <- coeftest(Vote_Model_13, vcov = vcovHC(Vote_Model_13, type = "HC3"))
Vote_Model_13_robust 

Vote_Model_13_Stand <- lm(vote_n ~ condition*income_c, data = zdf)
summary(Vote_Model_13_Stand) 

# Use two tailed lm function to format
Vote_Model_13_Results <- format_lm_bin_output_twotailed(Vote_Model_13_robust,Vote_Model_13_Stand)

# Outputs:
Vote_Model_13_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_13_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

##

# Low income

Vote_Model_14 <- lm(vote_n ~ condition*income_low, data = df)
summary(Vote_Model_14) 

Vote_Model_14_robust <- coeftest(Vote_Model_14, vcov = vcovHC(Vote_Model_14, type = "HC3"))
Vote_Model_14_robust 

Vote_Model_14_Stand <- lm(vote_n ~ condition*income_low, data = zdf)
summary(Vote_Model_14_Stand) 

# Use two tailed lm function to format
Vote_Model_14_Results <- format_lm_bin_output_twotailed(Vote_Model_14_robust,Vote_Model_14_Stand)

# Outputs:
Vote_Model_14_Results$appendix   # Cleaned and formatted for LaTeX

##

# High income

Vote_Model_15 <- lm(vote_n ~ condition*income_high, data = df)
summary(Vote_Model_15) 

Vote_Model_15_robust <- coeftest(Vote_Model_15, vcov = vcovHC(Vote_Model_15, type = "HC3"))
Vote_Model_15_robust 

Vote_Model_15_Stand <- lm(vote_n ~ condition*income_high, data = zdf)
summary(Vote_Model_15_Stand) 

# Use two tailed lm function to format
Vote_Model_15_Results <- format_lm_bin_output_twotailed(Vote_Model_15_robust,Vote_Model_15_Stand)

# Outputs:
Vote_Model_15_Results$appendix   # Cleaned and formatted for LaTeX

```

```{r, Voting Interaction with Education Two-Tailed}

# Condition*education
Vote_Model_16 <- lm(vote_n ~ condition*edu_c, data = df)
summary(Vote_Model_16) 

Vote_Model_16_robust <- coeftest(Vote_Model_16, vcov = vcovHC(Vote_Model_16, type = "HC3"))
Vote_Model_16_robust 

Vote_Model_16_Stand <- lm(vote_n ~ condition*edu_c, data = zdf)
summary(Vote_Model_16_Stand) 

# Use two tailed lm function to format
Vote_Model_16_Results <- format_lm_bin_output_twotailed(Vote_Model_16_robust, Vote_Model_16_Stand)

# Outputs:
Vote_Model_16_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_16_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Pre-Intention to Register

```{r, Voting Interaction with Pre-Intention to Register Two-Tailed}

# Test the interaction with pre-intention to register
Vote_Model_17 <- lm(vote_n ~ condition*pre_intention_c, data = df)
summary(Vote_Model_17) 

Vote_Model_17_robust <- coeftest(Vote_Model_17, vcov = vcovHC(Vote_Model_17, type = "HC3"))
Vote_Model_17_robust

Vote_Model_17_Stand <- lm(vote_n ~ condition*pre_intention_c, data = zdf)
summary(Vote_Model_17_Stand) 

# Use two tailed lm function to format
Vote_Model_17_Results <- format_lm_bin_output_twotailed(Vote_Model_17_robust, Vote_Model_17_Stand)

# Outputs:
Vote_Model_17_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_17_Results$appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# Interest

```{r, Voting Interaction with Interest Two-Tailed}

# Test the interaction with interest
Vote_Model_18 <- lm(vote_n ~ condition*interest_c, data = df)
summary(Vote_Model_18) 

Vote_Model_18_robust <- coeftest(Vote_Model_18, vcov = vcovHC(Vote_Model_18, type = "HC3"))
Vote_Model_18_robust 

Vote_Model_18_Stand <- lm(vote_n ~ condition*interest_c, data = zdf)
summary(Vote_Model_18_Stand) 

# Use two tailed glm function to format
Vote_Model_18_Results <- format_lm_bin_output_twotailed(Vote_Model_18_robust, Vote_Model_18_Stand)

# Outputs:
Vote_Model_18_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_18_Results$appendix_xtable, include.rownames = FALSE)

```

# Knowledge

```{r, Voting Interaction with Knowledge Two-Tailed}

# Test the interaction with knowledge
Vote_Model_19 <- lm(vote_n ~ condition*knowledge_c, data = df)
summary(Vote_Model_19)  

Vote_Model_19_robust <- coeftest(Vote_Model_19, vcov = vcovHC(Vote_Model_19, type = "HC3"))
Vote_Model_19_robust 

Vote_Model_19_Stand <- lm(vote_n ~ condition*knowledge_c, data = zdf)
summary(Vote_Model_19_Stand)  

# Use two tailed lm function to format
Vote_Model_19_Results <- format_lm_bin_output_twotailed(Vote_Model_19_robust, Vote_Model_19_Stand)

# Outputs:
Vote_Model_19_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_19_Results$appendix_xtable, include.rownames = FALSE)

```

# Cost of Voting Index (COVI)

```{r, Voting Interaction with COVI Two-Tailed}

# Test the interaction with COVI score
Vote_Model_20 <- lm(vote_n ~ condition*COVI_c, data = df)
summary(Vote_Model_20) 

Vote_Model_20_robust <- coeftest(Vote_Model_20, vcov = vcovHC(Vote_Model_20, type = "HC3"))
Vote_Model_20_robust 

Vote_Model_20_Stand <- lm(vote_n ~ condition*COVI_c, data = zdf)
summary(Vote_Model_20_Stand) 

# Use two tailed glm function to format
Vote_Model_20_Results <- format_lm_bin_output_twotailed(Vote_Model_20_robust, Vote_Model_20_Stand)

# Outputs:
Vote_Model_20_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_20_Results$appendix_xtable, include.rownames = FALSE)

##

# Low COVI

# Test the interaction with COVI score
Vote_Model_21 <- lm(vote_n ~ condition*COVI_low, data = df)
summary(Vote_Model_21) 

Vote_Model_21_robust <- coeftest(Vote_Model_21, vcov = vcovHC(Vote_Model_21, type = "HC3"))
Vote_Model_21_robust 

Vote_Model_21_Stand <- lm(vote_n ~ condition*COVI_low, data = zdf)
summary(Vote_Model_21_Stand) 

# Use two tailed glm function to format
Vote_Model_21_Results <- format_lm_bin_output_twotailed(Vote_Model_21_robust, Vote_Model_21_Stand)

# Outputs:
Vote_Model_21_Results$appendix   # Cleaned and formatted for LaTeX

##

# High COVI

# Test the interaction with COVI score
Vote_Model_22 <- lm(vote_n ~ condition*COVI_high, data = df)
summary(Vote_Model_22) 

Vote_Model_22_robust <- coeftest(Vote_Model_22, vcov = vcovHC(Vote_Model_22, type = "HC3"))
Vote_Model_22_robust 

Vote_Model_22_Stand <- lm(vote_n ~ condition*COVI_high, data = zdf)
summary(Vote_Model_22_Stand) 

# Use two tailed glm function to format
Vote_Model_22_Results <- format_lm_bin_output_twotailed(Vote_Model_22_robust, Vote_Model_22_Stand)

# Outputs:
Vote_Model_22_Results$appendix   # Cleaned and formatted for LaTeX

```

# By Region

```{r, Voting Interaction with Region Two-Tailed}

# Interaction with region
Vote_Model_23 <- lm(vote_n ~ condition*region, data = df)
summary(Vote_Model_23) 

# Means within each region
votemeansregion <- emmeans(Vote_Model_23, ~ condition | region, level = 0.95)

# Condition differences by region
votecomparecond <- as.data.frame(pairs(votemeansregion, adjust = "None", by = "region")) %>%
  filter(grepl("ControlCondition", contrast)) # Only keep comparisons with the control condition

votecomparecond

# Apply formatting and sorting
votecomparecond_clean <- votecomparecond %>%
  mutate(
    Contrast = contrast,
    'PP Inc.' = sprintf("%.2f", -100*estimate),
    b = sprintf("%.2f", -1*estimate),
    SE = sprintf("%.2f", SE),
    t = sprintf("%.2f", -1*t.ratio),
    p = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value))),
    p.value_two = ifelse(p.value < 0.001, "<.001", sub("^0\\.", ".", sprintf("%.3f", p.value)))) %>%
    dplyr::select(Contrast, 'PP Inc.', b, SE, t, p)

votecomparecond_clean

# For latex
align_spec <- c("l", "l", "r", "r", "r", "r", "r")

votecomparecond_clean_appendix_xtable <- xtable(votecomparecond_clean, align = align_spec, include.rownames = FALSE, sanitize.colnames.function = identity, sanitize.text.function = identity, floating = FALSE)

print.xtable(votecomparecond_clean_appendix_xtable, include.rownames = FALSE) # Syntax for latex editor

```

# By Swing State

```{r, Voting Interaction with Swing State}

# Interaction with swing state status
Vote_Model_24 <- lm(vote_n ~ condition*swing_E, data = df)
summary(Vote_Model_24) 

Vote_Model_24_robust <- coeftest(Vote_Model_24, vcov = vcovHC(Vote_Model_24, type = "HC3"))
Vote_Model_24_robust 

Vote_Model_24_Stand <- lm(vote_n ~ condition*swing_E, data = zdf)
summary(Vote_Model_24_Stand)

# Use two tailed lm function to format
Vote_Model_24_Results <- format_lm_bin_output_twotailed(Vote_Model_24_robust, Vote_Model_24_Stand)

# Outputs:
Vote_Model_24_Results$appendix   # Cleaned and formatted for LaTeX

print.xtable(Vote_Model_24_Results$appendix_xtable, include.rownames = FALSE)

```

################################################################################################################
####################################### Associations between Primary DVs #######################################
################################################################################################################

```{r, Correlations Between DVs}

# Just in the control condition
df_control_sub <- df %>%
  dplyr::filter(condition == "ControlCondition") # control condition only

# Association between link clicks and registration
cor.test(df_control_sub$linkClicked_n, df_control_sub$register_n) # r = 0.09, p-value = .002

# Association between voting intentions and voting 
cor.test(df$voteInt, df$vote_n) # r = 0.11, p-value < 2.2e-16

##

# Proportion of people who voted of those registered, in the whole sample
df %>% 
  filter(register_n == 1) %>% 
  dplyr::summarise(vote_n = mean(vote_n, na.rm = TRUE))  # Proportion who voted

# 0.38
# Among participants who we registered, 38% reported voting. 

```

################################################################################################################
########################################### Effect size correlations ###########################################
################################################################################################################

```{r, Effect Size Correlations - All DVs}

# Correlate effect sizes between DVs

conditions <- c("Distrust Salience", "Correcting Misperceptions", "Dynamic Norms", 
                "Self-Generated Norms", "System Justification", "Escalating Commitment", 
                "Personal Importance", "Interdependent Construal", "Moral Reasons", 
                "Implementation Intentions")

# Function to clean up results 
clean_results <- function(df, outcome_name) {
  df %>%
    mutate(
      Variable = str_trim(Variable),
      d = as.numeric(d) # Make sure Cohen's d numeric 
    ) %>%
    filter(Variable %in% conditions) %>% # Only keep conditions
    transmute(Intervention = Variable,
              Outcome = outcome_name,
              d)
}

# Apply to each table
link_tbl <- clean_results(Link_Model_1_Results$appendix, "Link")
intent_tbl <- clean_results(Intentions_Model_1_Results$appendix, "Intentions")
reg_tbl <- clean_results(Registration_Model_1_Results$appendix,"Registration")
vote_tbl <- clean_results(Vote_Model_1_Results$appendix,"Voting")

trust_tbl <- clean_results(TrustAgg_Model_1_Results$appendix,"Trust")
efficacy_tbl <- clean_results(Efficacy_Model_1_Results$appendix,"Efficacy")
norms_tbl <- clean_results(Norms_Model_1_Results$appendix,"Norms")

# Merge results 
all_ds <- bind_rows(intent_tbl, link_tbl, reg_tbl, vote_tbl, trust_tbl, efficacy_tbl, norms_tbl) # Long format

# Make wide 
all_ds_wide <- all_ds %>%
  pivot_wider(names_from = Outcome, values_from = d)

all_ds_wide

# Correlation matrix
d_mat <- all_ds_wide %>%  # Create data frame with just numbers 
  dplyr::select(-Intervention) %>% 
  as.data.frame()

cor_mat  <- cor(d_mat, use = "pairwise.complete.obs")
p_mat <- cor_pmat(d_mat)

# Blank upper triangle 
cor_mat[upper.tri(cor_mat)] <- NA
p_mat[upper.tri(p_mat)] <- NA

# Significance stars
get_stars <- function(p) {
  ifelse(is.na(p), "", 
         ifelse(p < 0.001, "***", 
         ifelse(p < 0.01, "**", 
         ifelse(p < 0.05, "*", ""))))
}

# Format correlations (round, remove leading 0s, add stars)
formatted_cor <- matrix("", nrow = nrow(cor_mat), ncol = ncol(cor_mat),
                        dimnames = dimnames(cor_mat))

for (i in 1:nrow(cor_mat)) {
  for (j in 1:ncol(cor_mat)) {
    val <- cor_mat[i, j]
    if (!is.na(val)) {
      stars <- get_stars(p_mat[i, j])
      val_fmt <- sprintf("%.2f", val)
      val_fmt <- sub("^-0\\.", "-.", val_fmt)   # remove leading 0 
      val_fmt <- sub("^0\\.", ".", val_fmt)     
      formatted_cor[i, j] <- paste0(val_fmt, stars)
    }
  }
}

formatted_cor

# Visualize 
pdf(file = "EffectSizeCorrs.pdf")
corrplot(cor_mat, method = 'circle', type = 'lower',addCoef.col ='black',
         title = "Effect Size Correlations Across All Dependent Measures",
         mar = c(0,0,1,0), number.cex = 0.8, number.digits = 2)
dev.off()

```

# Don analysis (delete?)

```{r, Don Analyses}
  
# Create each of the categories 
df$sequence <- NA

# 0. Don’t click, don’t register, don’t vote 
# 1. Click, don’t register, don’t vote
# 2. Click, register, don’t vote 
# 3. Don’t click, register, don’t vote 
# 4. Don’t click, register, vote 
# 5. Click, register, vote


df <- df %>%
  mutate(
    # Create engagement sequence
    engagement_seq = case_when(
      linkClicked_n == 0 & register_n == 0 & vote_n == 0 ~ 0, # 0. Don’t click, don’t register, don’t vote 
      linkClicked_n == 1 & register_n == 0 & vote_n == 0 ~ 1, # 1. Click, don’t register, don’t vote
      linkClicked_n == 1 & register_n == 1 & vote_n == 0 ~ 2, # 2. Click, register, don’t vote 
      linkClicked_n == 0 & register_n == 1 & vote_n == 0 ~ 3, # 3. Don’t click, register, don’t vote 
      linkClicked_n == 0 & register_n == 1 & vote_n == 1 ~ 4, # 4. Don’t click, register, vote 
      linkClicked_n == 1 & register_n == 1 & vote_n == 1 ~ 5, # 5. Click, register, vote
      TRUE ~ NA_real_  # catch any missing or odd cases
    ))

table(df$engagement_seq)


# OLS version
Seq_Model_1 <- lm(engagement_seq ~ condition, data = df)
summary(Seq_Model_1)


# Multinomial version 

# Ensure categorical variables are properly formatted
df$engagement_seq = factor(df$engagement_seq, levels = 0:5,
                        labels = c("No click/register/vote", "Click only",
                                   "Click + register", "Register (no click)",
                                   "Register + vote (no click)", 
                                   "Click + register + vote"))

table(df$engagement_seq)

# Fit the multinomial logistic regression model with the new reference categories
# The model compares all categories to no click, no register, no vote
Seq_Model_2 <- multinom(engagement_seq ~ condition, data = df)
summary(Seq_Model_2)

# Compute Wald z-values to get p values
z_values <- summary(Seq_Model_2)$coefficients / summary(Seq_Model_2)$standard.errors

# Compute p-values from z-values
p_values <- 2 * (1 - pnorm(abs(z_values)))

# Combine results into a table
results <- data.frame(
  Coefficient = summary(Seq_Model_2)$coefficients,
  Std_Error = summary(Seq_Model_2)$standard.errors,
  Z_Value = z_values,
  P_Value = p_values
)
# Print results
results

```
